---
title: "2_pans_modelling"
author: "Jo Garrett"
date: "`r Sys.Date()`"
output: 
  officedown::rdocx_document
always_allow_html: true
---

```{r load_packages,echo =FALSE, message=FALSE, warning =FALSE}
## deleted from above output: word_document
library(officedown)
library(broom)
library(broom.helpers)
#library(car)
library(cowplot)
#library(DiagrammeR)

#library(DiagrammeRsvg)
library(dplyr)
library(fastDummies)
library(flextable)
library(forcats)
library(ggplot2)
library(ggeffects)
#library(glue)

library(gtsummary)

library(lavaan)

#library(lavaanPlot)
library(lmtest)
library(RColorBrewer)
#library(rmarkdown)
library(rsq)
#library(rsvg)

#library(survey)
library(tibble)
library(tidyr)
library(tidySEM)
library(VGAM)

#library(lavaan.survey)
```



```{r custom_tbl_function, echo = FALSE}
## Create custom functions for displaying model results
glm_tbl_regression<-function(model_output){
  tbl_regression(model_output, 
                 intercept = TRUE,
                 estimate_fun=function(x) style_number(x, digits=2), pvalue_fun=function(x) style_pvalue(x, digits=3)) %>%
    bold_p() %>%
    add_significance_stars(hide_ci=FALSE, hide_se = TRUE) %>%
    add_glance_table(label=list(AIC~"AIC", Rsq~"R2"), include = c(AIC, nobs, Rsq),
                     glance_fun=function(x) glance(x) %>% add_column(Rsq=rsq(x)))
}


## Custom model function for displaying logistical regression model results
bin_tbl_regression<-function(model_output){
  tbl_regression(model_output, 
                 exponentiate = TRUE,
                 intercept = TRUE,
                 estimate_fun=function(x) style_number(x, digits=2), pvalue_fun=function(x) style_pvalue(x, digits=3)) %>%
    bold_p() %>%
    add_significance_stars(hide_ci=FALSE, hide_se = TRUE) %>%
    add_glance_table(label=list(AIC~"AIC", Rsq~"R2"), include = c(AIC, nobs, Rsq),
                     glance_fun=function(x) glance(x) %>% add_column(Rsq=rsq(x)))
}
```


```{r read_data, echo = FALSE}

## Specify location of data generated using 2_pans_modelling.Rmd
Data_wd<-"E:\\Projects\\RENEW\\Jo\\PANS\\PANS_data"
Results_wd<-"E:\\Projects\\RENEW\\Jo\\PANS\\Results"
Figures_wd<-"E:\\Projects\\RENEW\\Jo\\PANS\\Figures"
setwd(Data_wd)

## Find most recently generated workspace
df_file_info <- data.frame(file.info(list.files(Data_wd, full.names = T, pattern ="pans_data_workspace_")), list.files(Data_wd, pattern ="pans_data_workspace_"))
ind<-which(df_file_info$mtime==max(df_file_info$mtime))


## Load most recent workspace
load(df_file_info[ind,8])

rm(ind, df_file_info)

mod_data$Gender<-as.factor(mod_data$Gender)
mod_data$Age_Band<-as.factor(mod_data$Age_Band) %>%
relevel(ref = "40-54")
```


<!---BLOCK_LANDSCAPE_START--->
# RQ1

## Outcome 1 - Composite measure of nearby nature qualities

```{r glm_comp_measure_nearby_nature, echo = FALSE, message=FALSE, warning=FALSE}


predictor_names<-c("Region", "Home_IMD_quint", 
                   "Income", "ACNG_A_pred_ptc_wtd_percent_cats",
                   "AH_A_pred_ptc_wtd_percent_cats", 
                   "BMYW_A_pred_ptc_wtd_percent_cats",
                   "BUAG_A_pred_ptc_wtd_percent_cats",
                   "IG_A_pred_ptc_wtd_percent_cats")
predictor_labels<-c("Region", "IMD", "Income",
                    "ACN grassland", "Arable", "Woodland",
                    "Built up and gardens","Improved grassland")
pred_code<-c("Region", "IMD", "Inc",
             "ACNG", "AH", "BMYW",
             "BUAG","IG")
predictor_names<-c(predictor_names, "num_habs_wtd")
pred_code<-c(pred_code, "Num")

print("Check factor levels for region, South East should be last")
levels(mod_data$Region)

## Run unadjusted models for each predictor
for (i in 1:length(predictor_names)){
  ## Generate unadjusted model formula
  mod_form<-reformulate(predictor_names[i], response = "M1_Q5_comp")
  ## Fit unadjusted model
  unadj_glm<-glm(mod_form, data = mod_data, contrasts = list(Region="contr.sum") )
  ## Save each unadjusted model in the environment
  assign(paste0("unadj_glm_comp_", pred_code[i]), unadj_glm)
  rm(unadj_glm, mod_form)
}

rm(i)

## Fit adjusted model predicting nearby nature qualities composite by land cover proportions
adj_glm_habs_comp<-glm(M1_Q5_comp ~Region +Home_IMD_quint + Income  + ACNG_A_pred_ptc_wtd_percent_cats+ AH_A_pred_ptc_wtd_percent_cats + BMYW_A_pred_ptc_wtd_percent_cats + BUAG_A_pred_ptc_wtd_percent_cats + IG_A_pred_ptc_wtd_percent_cats + Gender +  Age_Band +  Ethnicity_cats + Marital_cats +  car_cats+ Dog + Gen_health_3cats  + Illnesses + Year +covid_restrictions + season, data = mod_data, weights = rescaled_weights, contrasts = list(Region="contr.sum") )

base_adj_glm<-glm(M1_Q5_comp ~Region +Home_IMD_quint + Income  + Gender +  Age_Band +  Ethnicity_cats + Marital_cats +  car_cats+ Dog + Gen_health_3cats  + Illnesses + Year +covid_restrictions + season, data = mod_data, weights = rescaled_weights, contrasts = list(Region="contr.sum") )

anova_habs<-anova(base_adj_glm, adj_glm_habs_comp, test = "F")
delta_r2_habs <- rsq(adj_glm_habs_comp) - rsq(base_adj_glm)

## Generate model summary table
#adj_glm_habs_tbl<-glm_tbl_regression(adj_glm_habs)

## Fit adjusted model predicting nearby nature qualities composite by land cover number
adj_glm_num_hab_comp<-glm(M1_Q5_comp ~Region +Home_IMD_quint + Income  +  num_habs_wtd + Gender +  Age_Band +  Ethnicity_cats + Marital_cats +  car_cats+ Dog + Gen_health_3cats  + Illnesses + Year +covid_restrictions + season, data = mod_data,weights = rescaled_weights, contrasts = list(Region="contr.sum") )

anova_num_habs<-anova(base_adj_glm, adj_glm_num_hab_comp, test = "F")
delta_r2_num_habs <- rsq(adj_glm_num_hab_comp) - rsq(base_adj_glm)
rm(base_adj_glm)

## List all model objects
list_mods<-ls(pattern = "adj")

## Generate model summary tables for all models
for (i in 1:length(list_mods)){
  mod_tbl<-glm_tbl_regression(get(list_mods[i]))
  assign(paste0(list_mods[i], "_tbl"), mod_tbl)
}

```


```{r, plot_comp_mods, echo = FALSE}

# tidy models for plotting
list_mods <- ls(pattern = "adj.*hab")
list_mods <- list_mods[!grepl("tbl", list_mods)]

## Generate tidy model summaries

for (model_name in list_mods){
  mod_obj<-get(model_name)
  ## Tidy model object
  tidy_mod<- tidy(mod_obj) %>%
    as.data.frame()
  ## Get c95% confidence intervals
  confints_mods<-confint(mod_obj) %>%
    as.data.frame()
  ## Merge tidy model results and confidence intervals
  tidy_mod<-data.frame(tidy_mod, confints_mods)
  names(tidy_mod)[6:7]<-c("lwr", "upr")
  rm(confints_mods)
  
  ## Create new columns, with Variable and level/category
  terms<-attr(mod_obj$terms, "term.labels")
  tidy_mod$Variable<-NA
  tidy_mod$term_levels<-NA
  for (j in 1:length(terms)){
    ind<-grep(terms[j], tidy_mod$term)
    tidy_mod$Variable[ind]<-terms[j]
    tidy_mod$term_levels[ind]<- gsub(terms[j], "",tidy_mod$term[ind] )
    }
  tidy_mod$Variable<-as.factor(tidy_mod$Variable) %>%
    factor(levels=unique(tidy_mod$Variable))
    tidy_mod$term<-as.factor(tidy_mod$term) %>%
    factor(levels=unique(tidy_mod$term))
    ## Save tidy model results to environment
  assign(paste0("tidy_", model_name), tidy_mod)
  
}

rm(tidy_mod, model_name, list_mods, ind, terms, mod_obj, j)

## Rename region term levels 
ind<-grep("Region", tidy_adj_glm_habs_comp$Variable)
tidy_adj_glm_habs_comp$term_levels[ind]<-as.character(levels(mod_data$Region)[1:8])

ind<-grep("Region",tidy_adj_glm_num_hab_comp$Variable)
tidy_adj_glm_num_hab_comp$term_levels[ind]<-as.character(levels(mod_data$Region)[1:8])
rm(ind)

tidy_adj_glm_habs_comp$Variable<-gsub("Home_", "", tidy_adj_glm_habs_comp$Variable)
tidy_adj_glm_habs_comp$Variable<-gsub("_quint", "", tidy_adj_glm_habs_comp$Variable)
tidy_adj_glm_habs_comp$Variable<-gsub("_cats", "", tidy_adj_glm_habs_comp$Variable)
tidy_adj_glm_habs_comp$Variable<-gsub("_A_pred_ptc_wtd_percent", "", tidy_adj_glm_habs_comp$Variable)


tidy_adj_glm_num_hab_comp$Variable<-gsub("Home_", "", tidy_adj_glm_num_hab_comp$Variable)
tidy_adj_glm_num_hab_comp$Variable<-gsub("_quint", "", tidy_adj_glm_num_hab_comp$Variable)
tidy_adj_glm_num_hab_comp$Variable<-gsub("_cats", "", tidy_adj_glm_num_hab_comp$Variable)
tidy_adj_glm_num_hab_comp$Variable<-gsub("_A_pred_ptc_wtd_percent", "", tidy_adj_glm_num_hab_comp$Variable)

## plot 1 - region, household income and IMD coefficients based on the middle with habitats at LSOA


tidy_adj_glm_habs_comp$term_levels<-as.factor(tidy_adj_glm_habs_comp$term_levels) 
tidy_adj_glm_habs_comp$term_levels<-factor(tidy_adj_glm_habs_comp$term_levels,levels=levels(tidy_adj_glm_habs_comp$term_levels)[c(1:9, 13:14, 20:24, 10:12, 15,25:29,16:19,30:50)])

ind<-which(tidy_adj_glm_habs_comp$Variable=="ACNG")
tidy_adj_glm_habs_comp$Variable[ind]<-"ACN grassland"
ind<-which(tidy_adj_glm_habs_comp$Variable=="AH")
tidy_adj_glm_habs_comp$Variable[ind]<-"Arable"
ind<-which(tidy_adj_glm_habs_comp$Variable=="BMYW")
tidy_adj_glm_habs_comp$Variable[ind]<-"Woodland"
ind<-which(tidy_adj_glm_habs_comp$Variable=="IG")
tidy_adj_glm_habs_comp$Variable[ind]<-"Improved grassland"
ind<-which(tidy_adj_glm_habs_comp$Variable=="BUAG")
tidy_adj_glm_habs_comp$Variable[ind]<-"Built-up and Gardens"
rm(ind)

tidy_adj_glm_habs_comp$Variable<-as.factor(tidy_adj_glm_habs_comp$Variable)
tidy_adj_glm_habs_comp$Variable<-factor(tidy_adj_glm_habs_comp$Variable,levels = c("ACN grassland", "Built-up and Gardens", "Arable","IMD",  "Woodland" ,"Income", "Improved grassland" ,"Region"))

tidy_adj_glm_habs_comp$Significance<-"Not significant"
ind<-which(tidy_adj_glm_habs_comp$p.value<0.05)
tidy_adj_glm_habs_comp$Significance[ind]<-"Significant"
tidy_adj_glm_habs_comp$Significance<-as.factor(tidy_adj_glm_habs_comp$Significance)

## plot Adjusted results predicting the composite level of nearby nature qualities
p<-ggplot(tidy_adj_glm_habs_comp[2:37,], aes(x =term_levels, y = estimate, ymin = lwr, ymax = upr))+
  geom_pointrange(aes(shape = Significance))+
  theme_minimal()+
   scale_shape_manual(values = c(1, 19)) +
  facet_wrap(facets = vars(Variable), nrow = 4, scales = "free_y")+
  coord_flip()+
  geom_hline(yintercept=0,linetype="dashed", colour = "gray51")+
  ylab("Beta coefficient")+
  xlab("Variable levels")

# Save plot
p
setwd(Figures_wd)
ggsave("RQ1_nature_comp_adj_coefs.png", dpi = 300, height = 7.5, width = 8)

rm(tidy_adj_glm_habs_comp)
rm(list = ls(pattern = "tidy_unadj"))

## Plot predicted nearby nature qualities composite by number of habitats, adjusted
predict_num_habs<- predict_response(adj_glm_num_hab_comp, terms = "num_habs_wtd")
predict_num_habs_comp<-plot(predict_num_habs, facets = FALSE, show_title= FALSE)+
  xlab("Number of habitats")+
  ylab("Predicted composite score")+
  xlim(c(1, 17))

predict_num_habs_comp
# Save plot
setwd(Figures_wd)
ggsave("RQ1_nature_comp_adj_coefs_num_habs.png", dpi = 300, height = 4, width = 4.5)
list_unadj<-ls(pattern="unadj_glm")
list_unadj <- list_unadj[!grepl("tbl", list_unadj)]
rm(list = list_unadj)
rm(tidy_adj_glm_num_hab, p)

list_adj<-ls(pattern="adj_glm")
list_adj <- list_adj[!grepl("unadj", list_adj)]
list_adj <- list_adj[!grepl("tbl", list_adj)]

rm(list = list_adj)
rm(ind, predict_num_habs, list_unadj, list_adj)

```


<!---BLOCK_LANDSCAPE_START--->

# RQ1, Outcome 3 - Quality satisfaction



```{r glm_quality_satisfaction, echo = FALSE, warning = FALSE}

## Create binary outcome for nearby nature opportunities
mod_data$Nature_opp_met_bin<-mod_data$Nature_opp_met
ind<-which(mod_data$Nature_opp_met_bin=="No need")

## Exclude all those who have "no need" to be satisfied with nearby nature opportunities
mod_data$Nature_opp_met_bin[ind]<-NA
mod_data$Nature_opp_met_bin<-factor(mod_data$Nature_opp_met_bin, levels = c("Unsatisfied", "Satisfied"))

## Fit all unadjusted models
for (i in 1:length(predictor_names)){
  mod_form<-reformulate(predictor_names[i], response = "Nature_opp_met_bin")
  unadj_glm<-glm(mod_form, data = mod_data, contrasts = list(Region="contr.sum"), family = binomial )
  assign(paste0("unadj_glm_need_", pred_code[i]), unadj_glm)
  rm(unadj_glm, mod_form)
}

rm(i)

## Fit adjusted model
adj_glm_need<-glm(Nature_opp_met_bin~Region +Home_IMD_quint + Income  + ACNG_A_pred_ptc_wtd_percent_cats+ AH_A_pred_ptc_wtd_percent_cats + BMYW_A_pred_ptc_wtd_percent_cats + BUAG_A_pred_ptc_wtd_percent_cats + IG_A_pred_ptc_wtd_percent_cats + Gender +  Age_Band +  Ethnicity_cats + Marital_cats +  car_cats+ Dog + Gen_health_3cats  + Illnesses + Year +covid_restrictions  + season, data = mod_data, weights = rescaled_weights, contrasts = list(Region="contr.sum"), family = binomial )

base_glm_need<-glm(Nature_opp_met_bin~Region +Home_IMD_quint + Income  + Gender +  Age_Band +  Ethnicity_cats + Marital_cats +  car_cats+ Dog + Gen_health_3cats  + Illnesses + Year +covid_restrictions  + season, data = mod_data, weights = rescaled_weights, contrasts = list(Region="contr.sum"), family = binomial )


adj_glm_need_num<-glm(Nature_opp_met_bin ~Region +Home_IMD_quint + Income  + num_habs_wtd + Gender +  Age_Band +  Ethnicity_cats + Marital_cats +  car_cats+ Dog + Gen_health_3cats  + Illnesses + Year +covid_restrictions  + season , data = mod_data,weights = rescaled_weights, contrasts = list(Region="contr.sum"), family = binomial )

unadj_glm_need_num<-glm(Nature_opp_met_bin ~ num_habs_wtd  , data = mod_data,weights = rescaled_weights, family = binomial )

list_mods<-ls(pattern = "adj")
list_mods <- list_mods[!grepl("tbl", list_mods)]


## Generate gtsummary table for each fitted model
for (i in 1:length(list_mods)){
  mod_tbl<-bin_tbl_regression(get(list_mods[i]))
  assign(paste0(list_mods[i], "_tbl"), mod_tbl)
}

```



```{r merge_2_outcome_tables, echo = FALSE}


## Merge all unadjusted and adjusted tables

t_merge_all<-tbl_merge(tbls = list(unadj_glm_comp_Region_tbl, 
                               unadj_glm_comp_IMD_tbl,
                              unadj_glm_comp_Inc_tbl,
                             unadj_glm_comp_ACNG_tbl,
                               unadj_glm_comp_AH_tbl, 
                              unadj_glm_comp_BMYW_tbl,
                               unadj_glm_comp_BUAG_tbl,
                               unadj_glm_comp_IG_tbl,
                               adj_glm_habs_comp_tbl,
                             unadj_glm_need_Region_tbl,
                             unadj_glm_need_IMD_tbl,
                             unadj_glm_need_Inc_tbl,
                             unadj_glm_need_ACNG_tbl,
                             unadj_glm_need_AH_tbl,
                             unadj_glm_need_BMYW_tbl,
                             unadj_glm_need_BUAG_tbl,
                             unadj_glm_need_IG_tbl,
                             adj_glm_need_tbl
                             ), 
                   tab_spanner = c("Unadj comp- Region", "Unadj comp- IMD", "Unadj comp- income", "Unadj comp-ACNG", "Unadj comp-AH", "Unadj comp-BMYW","Unadj comp-BUAG","Unadj comp-IG", "comp Adj","Unadj need- Region", "Unadj need- IMD", "Unadj need- income", "Unadj need-ACNG", "Unadj need-AH", "Unadj need-BMYW","Unadj need-BUAG","Unadj need-IG", "need Adj")) %>%
  modify_table_body(
  ~ .x %>%
    arrange(row_type == "glance_statistic")) %>%
  as_flex_table() 

t_merge_all
rm(t_merge_all)
list_comp_tbls<-ls(pattern = "comp.*tbl")
list_comp_tbls <- list_comp_tbls[!grepl("num|Num", list_comp_tbls)]
rm(list =list_comp_tbls)
rm(list_comp_tbls)

print("Anova land covers")
anova_habs
print("R-squared difference")
delta_r2_habs
rm(anova_habs, delta_r2_habs)

print("Number of land covers")

## Merge all number of land cover model results tables for printing
t_merge_all_diversity<-tbl_merge(tbls = list(unadj_glm_comp_Num_tbl,
                              adj_glm_num_hab_comp_tbl,
                               unadj_glm_need_Num_tbl,
                               adj_glm_need_num_tbl), 
                   tab_spanner = c("Unadj comp", "Adj comp","Unadj need", "Adj need")) %>%
  modify_table_body(
  ~ .x %>%
    arrange(row_type == "glance_statistic")) %>%
  as_flex_table() 


## print table
t_merge_all_diversity
rm(t_merge_all_diversity)
print("Anova number of land covers")
anova_num_habs
print("Difference r squared number of land covers")
delta_r2_num_habs

list_tbls<-ls(pattern ="adj_glm.*tbl")
rm(list = list_tbls)
rm(t_merge_all, list_tbls, mod_tbl, i, anova_num_habs, delta_r2_num_habs)


lmtest::lrtest(base_glm_need ,adj_glm_need)

rsq(adj_glm_need) - rsq(base_glm_need)



```

<!---BLOCK_LANDSCAPE_STOP--->

```{r plot_nature_need, echo = FALSE}

## Tidy model output
tidy_adj_glm_need<-tidy(adj_glm_need) %>%
  as.data.frame()
## Calculate odds ratios
tidy_adj_glm_need$OR<-exp(coef(adj_glm_need))
## Calculate confidence intervals
confints_mods<-confint(adj_glm_need) %>%
  as.data.frame()
## Merge tidy model output and confidence intervals
tidy_adj_glm_need<-data.frame(tidy_adj_glm_need, confints_mods)
rm(confints_mods)
names(tidy_adj_glm_need)[7:8]<-c("lwr", "upr")

##Tidy model output, by number of land covers
tidy_adj_glm_need_num<-tidy(adj_glm_need_num) %>%
  as.data.frame()
## Calculate odds ratios
tidy_adj_glm_need_num$OR<-exp(coef(adj_glm_need_num))
## Calculate confidence intervals
confints_mods<-confint(adj_glm_need_num) %>%
  as.data.frame()
## Merge tidy model output and confidence intervals
tidy_adj_glm_need_num<-data.frame(tidy_adj_glm_need_num, confints_mods)
rm(confints_mods)
names(tidy_adj_glm_need_num)[7:8]<-c("lwr", "upr")

## Add Variable names and response options
tidy_mod_list<-ls(pattern = "tidy_adj_glm")
mod_list<-gsub("tidy_","",tidy_mod_list)
for (i in 1:length(mod_list)){
  mod_obj<-get(mod_list[i])
  terms<-attr(mod_obj$terms, "term.labels")
  tidy_mod_obj<-get(tidy_mod_list[i])
  tidy_mod_obj$Variable<-NA
  tidy_mod_obj$term_levels<-NA
  for (j in 1:length(terms)){
    ind<-grep(terms[j], tidy_mod_obj$term)
    tidy_mod_obj$Variable[ind]<-terms[j]
    tidy_mod_obj$term_levels[ind]<- gsub(terms[j], "",tidy_mod_obj$term[ind] )
  }
tidy_mod_obj$Variable<-as.factor(tidy_mod_obj$Variable) %>%
  factor(levels=unique(tidy_mod_obj$Variable))
tidy_mod_obj$term<-as.factor(tidy_mod_obj$term) %>%
  factor(levels=unique(tidy_mod_obj$term))
assign(tidy_mod_list[i], tidy_mod_obj)
}

rm(tidy_mod_obj, mod_obj, mod_list, tidy_mod_list)

## Add Region levels
ind<-grep("Region", tidy_adj_glm_need$Variable)
 tidy_adj_glm_need$term_levels[ind]<-as.character(levels(mod_data$Region)[1:8])
ind<-grep("Region",tidy_adj_glm_need_num$Variable)
tidy_adj_glm_need_num$term_levels[ind]<-as.character(levels(mod_data$Region)[1:8])
rm(ind)

tidy_adj_glm_need$Variable<-gsub("Home_", "", tidy_adj_glm_need$Variable)
tidy_adj_glm_need$Variable<-gsub("_quint", "", tidy_adj_glm_need$Variable)
tidy_adj_glm_need$Variable<-gsub("_cats", "", tidy_adj_glm_need$Variable)
tidy_adj_glm_need$Variable<-gsub("_A_pred_ptc_wtd_percent", "", tidy_adj_glm_need$Variable)


tidy_adj_glm_need_num$Variable<-gsub("Home_", "", tidy_adj_glm_need_num$Variable)
tidy_adj_glm_need_num$Variable<-gsub("_quint", "", tidy_adj_glm_need_num$Variable)
tidy_adj_glm_need_num$Variable<-gsub("_cats", "", tidy_adj_glm_need_num$Variable)
tidy_adj_glm_need_num$Variable<-gsub("_A_pred_ptc_wtd_percent", "", tidy_adj_glm_need_num$Variable)

## plot 1 - region, household income and IMD coefficients based on the middle with habitats at LSOA

tidy_adj_glm_need$term_levels<-as.factor(tidy_adj_glm_need$term_levels) 
tidy_adj_glm_need$term_levels<-factor(tidy_adj_glm_need$term_levels,levels=levels(tidy_adj_glm_need$term_levels)[c(1:9,13:14, 20:24, 10:12,15:19,25:50)])

ind<-which(tidy_adj_glm_need$Variable=="ACNG")
tidy_adj_glm_need$Variable[ind]<-"ACN grassland"
ind<-which(tidy_adj_glm_need$Variable=="AH")
tidy_adj_glm_need$Variable[ind]<-"Arable"
ind<-which(tidy_adj_glm_need$Variable=="BMYW")
tidy_adj_glm_need$Variable[ind]<-"Woodland"
ind<-which(tidy_adj_glm_need$Variable=="IG")
tidy_adj_glm_need$Variable[ind]<-"Improved grassland"
ind<-which(tidy_adj_glm_need$Variable=="BUAG")
tidy_adj_glm_need$Variable[ind]<-"Built-up and Gardens"
rm(ind)

tidy_adj_glm_need$Variable<-as.factor(tidy_adj_glm_need$Variable)
tidy_adj_glm_need$Variable<-factor(tidy_adj_glm_need$Variable,levels = c("ACN grassland", "Built-up and Gardens", "Arable","IMD",  "Woodland" ,"Income", "Improved grassland" ,"Region"))

## Add significance info
tidy_adj_glm_need$Significance<-"Not significant"
ind<-which(tidy_adj_glm_need$p.value<0.05)
tidy_adj_glm_need$Significance[ind]<-"Significant"
tidy_adj_glm_need$Significance<-as.factor(tidy_adj_glm_need$Significance)
tidy_adj_glm_need$lwr_exp<-exp(tidy_adj_glm_need$lwr)
tidy_adj_glm_need$upr_exp<-exp(tidy_adj_glm_need$upr)

## Plot odds ratios predicting satisfaction with nearby nature opportunities by different land covers
p<-ggplot(tidy_adj_glm_need[2:37,], aes(x = term_levels, y= OR, ymin = lwr_exp, ymax = upr_exp))+
 geom_pointrange(aes(shape = Significance)) +
  scale_shape_manual(values = c(1, 19))+
  theme_minimal()+
  facet_wrap(facets=vars(Variable), drop = TRUE, scales = "free_y", ncol = 2) +
  coord_flip() +
  geom_hline(yintercept=1 ,linetype="dashed") +
  xlab("")+
  ylab("Odds ratio")

p
setwd(Figures_wd)
ggsave("RQ1_nature_sat_adj_ORs.png", dpi = 300, height = 7.5, width = 8)

predict_num_habs<- predict_response(adj_glm_need_num, terms = "num_habs_wtd")


## plot probability of satisfaction with nearby nature opportunities by number of land covers
predict_num_habs_need<-plot(predict_num_habs, facets = FALSE, show_title= FALSE)+
  xlab("Number of habitats")+
  ylab("Predicted probability")+
  xlim(c(1, 17))+
  ylim(c(0.65, 0.85))


plot_grid(predict_num_habs_comp, predict_num_habs_need, labels = c('A', 'B'), label_size = 12)

setwd(Figures_wd)
ggsave("RQ1_pred_plots_num_habs.png", dpi = 300, height = 4, width = 8)

rm(p,predict_num_habs_comp, predict_num_habs_need, i, j, ind, list_mods, mod_tbl, terms, predictor_names, predict_num_habs, short_lsoas_habs, predictor_labels, pred_code)
rm(list = ls(pattern = "unadj_glm"))
rm(list = ls(pattern = "adj_glm"))


##up to here, all checked, running knit
```


<!---BLOCK_LANDSCAPE_STOP--->
## Outcome 2 - Good opportunities to see nature

```{r func_print_models, echo = FALSE}
## Create custom functions for presenting cumulative link model results

tidy_vglm<-function(model_object){
  model_summary<-summary(model_object)
  tidy_coefs<-data.frame("Odds"=exp(coef(model_object)),exp(confint(model_object)),"pvalue"=model_summary@coef3[,4]) %>%
    mutate(odds_rounded=round(Odds, digits =2)) %>%
    mutate(odds_stars=as.character(odds_rounded))
  
  ind<-which(tidy_coefs$pvalue<0.05)
  tidy_coefs$odds_stars[ind]<-paste0(tidy_coefs$odds_rounded[ind], "*")
  ind<-which(tidy_coefs$pvalue<0.01)
  tidy_coefs$odds_stars[ind]<-paste0(tidy_coefs$odds_rounded[ind], "**")
  ind<-which(tidy_coefs$pvalue<0.001)
  tidy_coefs$odds_stars[ind]<-paste0(tidy_coefs$odds_rounded[ind], "***")
  tidy_coefs$odds_rounded<-NULL
  tidy_coefs$ci<-paste0("(",round(tidy_coefs$X2.5.., digits =2), ", ", round(tidy_coefs$X97.5.., digits=2),")")
  tidy_coefs$full_results<-paste(tidy_coefs$odds_stars,tidy_coefs$ci, sep = " ")
  tidy_coefs$terms<-rownames(tidy_coefs)
  tidy_coefs<-data.frame(tidy_coefs$terms, tidy_coefs$full_results)
  names(tidy_coefs)<-gsub("tidy_coefs\\.","",names(tidy_coefs))
  ind<- gregexpr(":", tidy_coefs$terms) %>%
       unlist()
  tidy_coefs$interval <-substr(tidy_coefs$terms, ind+1,nchar(tidy_coefs$terms))
  tidy_coefs$variable<-substr(tidy_coefs$terms,1, ind-1)
  ind<-which(nchar(tidy_coefs$interval)>1)
   tidy_coefs$variable[ind]<-tidy_coefs$interval[ind]
   tidy_coefs$interval[ind]<-"Parallel"
  rm(ind)
   tidy_coefs$terms<-NULL
  tidy_coefs<-pivot_wider(tidy_coefs, names_from = interval, values_from = 'full_results')
  return(tidy_coefs)
}

## Create custom function for calculating R squared for cumulative link models
vglm_rsq<-function(model_object, null_model){
  prsq<-1 - deviance(model_object) / deviance(null_model)
  return(prsq)
}


## Create custom function to add model fit information to coefficient table for cumulative link models
adding_model_info<-function(variable, model_object, null_model_object, tidy_model_object){
  X1<-c(round(AIC(model_object), digits = 2),
        signif(vglm_rsq(model_object, null_model_object), digits = 3))
  if ( NCOL(tidy_model_object)==5){
    to_add<-data.frame(variable,X1, "2" = rep(NA,2),
                     "3" = rep(NA,2),
                     "4" = rep(NA,2))
  } else if (NCOL(tidy_model_object)==6){
    to_add<-data.frame(variable,X1,"1"= rep(NA,2), "2" = rep(NA,2),
                     "3" = rep(NA,2),
                     "4" = rep(NA,2))
  }
  
  rm(X1)
  names(to_add)<-names(tidy_model_object)
  tidy_model_with_stats<-rbind(tidy_model_object, to_add)
  rm(to_add)
  return(tidy_model_with_stats)
}

```

## Non-parallel probit cumulative link models
### Unadjusted models
```{r vglms_unadj, echo = FALSE}

## Check level of region, reference value is the last one for sum contrasts, and this should be South East
#levels(mod_data$Region)

## Region unadjusted model
vglm_unadj_region<- vglm(local_good_nature_ord ~ Region,
                         family= VGAM::cumulative(link = "probitlink", parallel = FALSE, reverse = TRUE),
  data = mod_data,
              weights = mod_data$rescaled_weights, 
              maxit = 1000, contrasts = list(Region = "contr.sum"), model = TRUE)
tidy_vglm_unadj_region<-tidy_vglm(vglm_unadj_region)
tidy_vglm_unadj_region$variable[2:9]<-levels(mod_data$Region)[1:8]

vglm_unadj_IMD<- vglm(local_good_nature_ord ~Home_IMD_quint, family = cumulative(parallel = FALSE,link ="probitlink", reverse = TRUE), na.action = na.omit,
              data = mod_data, weights = rescaled_weights)
tidy_vglm_unadj_IMD<-tidy_vglm(vglm_unadj_IMD)

vglm_unadj_inc<- vglm(local_good_nature_ord ~Income, family = cumulative(parallel = FALSE,link ="probitlink", reverse = TRUE), na.action = na.omit,
              data = mod_data, weights = rescaled_weights)
tidy_vglm_unadj_inc<-tidy_vglm(vglm_unadj_inc)

pcs_habs_cats<-c("ACNG_A_pred_ptc_wtd_percent_cats","AH_A_pred_ptc_wtd_percent_cats", "BMYW_A_pred_ptc_wtd_percent_cats", "BUAG_A_pred_ptc_wtd_percent_cats", "IG_A_pred_ptc_wtd_percent_cats")

short_lsoas_habs<-c("ACNG", "AH", "BMYW", "BUAG","IG","num")

## Carry out undjusted vglms for all land cover categories
for (i in 1:length(pcs_habs_cats)){
   formula <- reformulate(pcs_habs_cats[i],response = "local_good_nature_ord")
   vglm_obj<-vglm(formula, family = cumulative(parallel = FALSE,link = "probitlink", reverse = TRUE), na.action = na.omit,
              data = mod_data, weights = rescaled_weights)
   assign(paste0("vglm_unadj_", short_lsoas_habs[i], "_pcs_cats"),   vglm_obj)
   tidy_vglm_obj<-tidy_vglm(vglm_obj)
    assign(paste0("tidy_vglm_unadj_", short_lsoas_habs[i]),   tidy_vglm_obj)
    rm(tidy_vglm_obj, vglm_obj, formula)
}
rm(i)

```

### Adjusted models
```{r adj_model_vglm,echo = FALSE, warning = FALSE, fig.width = 5, fig.height = 3}

## Adjusted model with region, IMD, household income, land cover categories and all covariates
adj_vglm<-vglm(local_good_nature_ord ~ Region +Home_IMD_quint + Income  +ACNG_A_pred_ptc_wtd_percent_cats + AH_A_pred_ptc_wtd_percent_cats +BMYW_A_pred_ptc_wtd_percent_cats + BUAG_A_pred_ptc_wtd_percent_cats + IG_A_pred_ptc_wtd_percent_cats + Gender +  Age_Band +  Ethnicity_cats + Marital_cats +  car_cats+ Dog + Gen_health_3cats  + Illnesses + Year + season + covid_restrictions, family = cumulative(link = "probitlink", parallel =FALSE,reverse = TRUE), data =mod_data, weights = rescaled_weights, contrasts = list(Region = "contr.sum"))

tidy_adj_vglm<-tidy_vglm(adj_vglm)
tidy_adj_vglm$variable[2:9]<-levels(mod_data$Region)[1:8]


## Name all intercepts with predictor variable for later merging
list_tidy_unadj<-ls(pattern = "tidy_vglm_unadj")
for (i in 1:length(list_tidy_unadj)){
  obj <- get(list_tidy_unadj[i])   
  obj$variable[1] <- paste0("Intercept_", gsub("tidy_vglm_unadj_","", list_tidy_unadj[i]))
  assign(list_tidy_unadj[i], obj)
}

rm(list_tidy_unadj, obj, i)


## Carry out null model for later model fit statistics
null<- vglm(local_good_nature_ord ~1 ,
                         family= VGAM::cumulative(link = "probitlink", parallel = FALSE, reverse = TRUE),
  data = mod_data,
              weights = mod_data$rescaled_weights, 
              maxit = 1000)

variable<-c("AIC_region","region_rsq")
tidy_vglm_unadj_region<-adding_model_info(variable, vglm_unadj_region, null, tidy_vglm_unadj_region)

variable<-c("AIC_IMD","IMD_rsq")
tidy_vglm_unadj_IMD<-adding_model_info(variable, vglm_unadj_IMD, null, tidy_vglm_unadj_IMD)

variable<-c("AIC_inc","inc_rsq")
tidy_vglm_unadj_inc<-adding_model_info(variable, vglm_unadj_inc, null, tidy_vglm_unadj_inc)
rm(variable)

## Short land cover names
short_lcs<-c("ACNG", "AH", "BMYW", "BUAG", "IG")

## Add rsq and AIC to land cover models
for (i in 1:length(short_lcs)){
  variable<-c(paste0("AIC_", short_lcs[i]),paste0("rsq_", short_lcs[i]))
  unadj_mod<-adding_model_info(variable,get(paste0( "vglm_unadj_",short_lcs[i], "_pcs_cats")), null, get(paste0( "tidy_vglm_unadj_",short_lcs[i])))
  assign(paste0( "tidy_vglm_unadj_",short_lcs[i]), unadj_mod)
  rm(variable, unadj_mod)
}

list_tidy_unadj <-ls(pattern = "tidy_vglm_unadj")
list_tidy_unadj<-list_tidy_unadj[c(8, 6, 7, 1:5)]

## Put all unadj models together in a single data.frame
all_unadj <- do.call(rbind, mget(list_tidy_unadj, inherits = TRUE))

names(all_unadj)[2:5]<-paste0("unadj_",names(all_unadj)[2:5])
rm(list_tidy_unadj)

names(tidy_adj_vglm)[2:5]<-paste0("adj_",names(tidy_adj_vglm)[2:5])

all_unadj$variable<-as.factor(all_unadj$variable)
all_unadj$variable<-factor(all_unadj$variable, levels = unique(all_unadj$variable))

## Add model fit statistics to adjusted model results
variable<-c("AIC_adj","adj_rsq")
tidy_adj_vglm<-adding_model_info(variable, adj_vglm, null, tidy_adj_vglm)
rm(variable)

tidy_adj_vglm$variable<-as.factor(tidy_adj_vglm$variable)
tidy_adj_vglm$variable<-factor(tidy_adj_vglm$variable, levels = unique(tidy_adj_vglm$variable))

## Merge all unadjusted and adjusted results together in the same data.frame
all_results<-merge(all_unadj, tidy_adj_vglm, all = TRUE)


## Save all results 
setwd(Results_wd)
write.csv(all_results, "RQ1_nearby_nature_opps_vglm_results.csv")



```

## Unadjusted and adjusted number of land covers vglms
```{r num_habs_rq1, echo = FALSE}

## Unadjusted land cover diversity vglm
unadj_vglm_num_habs<-vglm(local_good_nature_ord ~ num_habs_wtd, family = cumulative(link = "probitlink", parallel =FALSE,reverse = TRUE), data = mod_data, weights = rescaled_weights)

## Adjuseted land cover diversity vglm
adj_vglm_num_habs<-vglm(local_good_nature_ord ~ Region +Home_IMD_quint + Income  +  num_habs_wtd + Gender +  Age_Band +  Ethnicity_cats + Marital_cats +  car_cats + Dog + Gen_health_3cats  + Illnesses + Year +covid_restrictions + season, family = cumulative(link = "probitlink", parallel =FALSE,reverse = TRUE), data = mod_data, weights = rescaled_weights, contrasts = list(Region = "contr.sum"))


## Tidy model results
tidy_unadj_vglm_num_habs<-tidy_vglm(unadj_vglm_num_habs)
tidy_adj_vglm_num_habs<-tidy_vglm(adj_vglm_num_habs)
tidy_adj_vglm_num_habs$variable[2:9]<-levels(mod_data$Region)[1:8]


## Add AIC pseudoR2 to tidy model results
variable<-c("AIC_unadj","unadj_rsq")
tidy_unadj_vglm_num_habs<-adding_model_info(variable, unadj_vglm_num_habs, null, tidy_unadj_vglm_num_habs)

variable<-c("AIC_adj","adj_rsq")
tidy_adj_vglm_num_habs<-adding_model_info(variable, adj_vglm_num_habs, null, tidy_adj_vglm_num_habs)


names(tidy_unadj_vglm_num_habs)[2:5]<-paste0("unadj_",names(tidy_unadj_vglm_num_habs)[2:5])

names(tidy_adj_vglm_num_habs)[2:5]<-paste0("adj_",names(tidy_adj_vglm_num_habs)[2:5])
rm(variable)

tidy_unadj_vglm_num_habs$variable<-as.factor(tidy_unadj_vglm_num_habs$variable) %>%
  factor( levels = unique(tidy_unadj_vglm_num_habs$variable))

tidy_adj_vglm_num_habs$variable<-as.factor(tidy_adj_vglm_num_habs$variable) %>% 
  factor( levels = unique(tidy_adj_vglm_num_habs$variable))

all_results_num_habs<-merge(tidy_unadj_vglm_num_habs, tidy_adj_vglm_num_habs, all = TRUE)

setwd(Results_wd)
write.csv(all_results_num_habs, "all_results_num_habs_RQ1.csv")

rm(null)

```

```{r custom_plot_functions, echo = FALSE}


# Create custom plot functions for plotting vglms
create_new_data<-function(predictor_data, terms, predictor_name){
  if (predictor_name=="num_habs_wtd"){
    num_habs_seq<-seq(min(predictor_data), max(predictor_data))
     new_data_df<-data.frame(matrix(NA,
                                   nrow = length(num_habs_seq),
                                   ncol = length(terms)))
     names(new_data_df)<-terms
      new_data_df[[predictor_name]]<-num_habs_seq
      rm(num_habs_seq)
  } else if (predictor_name!="BUAG_A_pred_ptc_wtd_percent_cats"){
    new_data_df<-data.frame(matrix(NA,
                                   nrow = length(levels(predictor_data)),
                                   ncol = length(terms)))
    names(new_data_df)<-terms
    new_data_df[[predictor_name]]<-levels(predictor_data)
  } else if (predictor_name=="BUAG_A_pred_ptc_wtd_percent_cats") {
    new_data_df<-data.frame(matrix(NA,
                                   nrow =  length(levels(predictor_data))-1,
                                   ncol = length(terms)))
    names(new_data_df)<-terms
    new_data_df[[predictor_name]]<-levels(mod_data[[predictor_name]])[2:5]
  }
  #Find all columns except the predictor column.
  #For each of those other columns, replace their values with the first level of the corresponding column in mod_data.
  col_ind<-which(names(new_data_df)!=predictor_name)
  
  for (i in col_ind) {
    col_name <- names(new_data_df)[i]
    new_data_df[[col_name]] <- rep(levels(mod_data[[col_name]])[1], nrow(new_data_df))
  }

  
  rm(col_ind, i)
  return(new_data_df)
}


predict_for_plots<-function(new_data_df,predictor_name,  model_object, outcome_data){
  predictions_vglm<- predictvglm(model_object, newdata = new_data_df, type = "response") %>%
    as.data.frame()
  fam<-model_object@family
  fam_inv<-fam@linkinv
  rm(fam)
  pred_link<-predictvglm(model_object,
                         newdata = new_data_df, 
                         type = "link",se.fit = TRUE)
  
  se_fit<-pred_link$se.fit
  fit_link<-pred_link$fitted.values
  rm(pred_link)
  
  upr = fam_inv(fit_link + (2 * se_fit))
  lwr = fam_inv(fit_link - (2 * se_fit))
  upr_df<-data.frame(upr, "Variable"=new_data_df[[predictor_name]])
  names(upr_df)[1:5]<-levels(outcome_data)
  
  lwr_df<-data.frame(lwr, "Variable"=new_data_df[[predictor_name]])
  names(lwr_df)[1:5]<-levels(outcome_data)
  rm(fam_inv, fit_link, se_fit, upr, lwr)
  predictions_vglm$Variable<-new_data_df[[predictor_name]]
  #predictions_vglm$Variable<-new_data_df$Region
  predictions_vglm<-pivot_longer(predictions_vglm, 
                                 !Variable, names_to = "Response", 
                                 values_to = "Predictions")
  lwr_df<-pivot_longer(lwr_df, !Variable, 
                       names_to = "Response", values_to = "lwr")
  upr_df<-pivot_longer(upr_df, !Variable, names_to = "Response", 
                       values_to = "upr")
  predictions_vglm<-base::merge(predictions_vglm, 
                          lwr_df, by = c("Variable", "Response"))
  rm(lwr_df)
  predictions_vglm<-merge(predictions_vglm,
                          upr_df, by = c("Variable", "Response"))
  rm(upr_df)
  predictions_vglm$Response<-as.factor(predictions_vglm$Response)
  predictions_vglm$Response<-factor(predictions_vglm$Response, levels = levels(outcome_data)) 
  
  coefs_model<-summary(model_object)@coef3 %>%
    as.data.frame()
  coefs_model$term<-rownames(coefs_model)
  predictions_vglm$Significance<-"Not significant"
  ind<-which(predictions_vglm$Response=="Strongly disagree")
  predictions_vglm$Significance[ind]<-"Reference"
  rm(ind)
  ind<-gregexpr(pattern =':',coefs_model$term) %>%
    unlist()
  end_ind<-nchar(coefs_model$term)
  coefs_model$Response<-substr(coefs_model$term, ind+1, end_ind) %>%
    as.factor() %>%
    fct_recode("Disagree" = "1", "Neither agree nor disagree"= "2",
               "Agree" = "3", "Strongly agree"= "4")
  rm(ind, end_ind)  
  ind<-grep(predictor_name, coefs_model$term)
  coefs_model<-coefs_model[ind,]
  coefs_model$Variable<-NA
  if (class(new_data_df[[predictor_name]])=="factor"){
    if (predictor_name=="Region"){
      i = seq(1,length(levels(mod_data$Region)[1:8]))
    } else {
      i = 1:length(levels(mod_data[[predictor_name]])[2:length(levels(mod_data[[predictor_name]]))])
    }
    start_ind<-4*i-3
    end_ind<-start_ind+3
    rm(i)
    if (predictor_name=="Region"){
      for (i in 1:length(levels(mod_data$Region)[1:8])){
        coefs_model$Variable[start_ind[i]:end_ind[i]]<-rep(levels(mod_data$Region)[i])
      }
    }else if (predictor_name=="BUAG_A_pred_ptc_wtd_percent_cats"){
      for (i in 1:(length(levels(mod_data$BUAG_A_pred_ptc_wtd_percent_cats))-2)){
        coefs_model$Variable[start_ind[i]:end_ind[i]]<-rep(levels(mod_data$BUAG_A_pred_ptc_wtd_percent_cats)[i+2])
      } 
    }else {
      for (i in 1:(length(levels(mod_data[[predictor_name]]))-1)){
        coefs_model$Variable[start_ind[i]:end_ind[i]]<-rep(levels(mod_data[[predictor_name]])[i+1])
      }
    }
    
    rm(end_ind, start_ind, i)
    predictions_vglm<-full_join(predictions_vglm, coefs_model, 
                                by= c("Variable", "Response")) %>%
      select(Variable, Response, Predictions, lwr, upr,
             Significance, 'Pr(>|z|)')
    ind<-which(predictions_vglm$`Pr(>|z|)`<0.05)
    predictions_vglm$Significance[ind]<-"Significant"
    if (predictor_name=="Region"){
      ind<-which(predictions_vglm$Variable==levels(mod_data[[predictor_name]])[9])
    } else if (predictor_name=="BUAG_A_pred_ptc_wtd_percent_cats"){
      ind<-which(predictions_vglm$Variable==levels(mod_data[[predictor_name]])[2])
    } else {
      ind<-which(predictions_vglm$Variable==levels(mod_data[[predictor_name]])[1])
    }
    predictions_vglm$Significance[ind]<-"Reference"
  } else{
    # predictions_vglm
    coefs_model$Variable<-NULL
    predictions_vglm<-full_join(predictions_vglm, coefs_model, 
                                by= "Response") %>%
      select(Variable, Response, Predictions, lwr, upr,
             Significance, 'Pr(>|z|)')
    ind<-which(predictions_vglm$`Pr(>|z|)`<0.05)
    predictions_vglm$Significance[ind]<-"Significant"
    
  }
  return(predictions_vglm)
}


plot_by_predictor_sorted<-function(predictions_vglm,  predictor_name){
    predictions_vglm$Response<-fct_recode(predictions_vglm$Response,"Neither"="Neither agree nor disagree")
  predictions_vglm$Variable<-as.factor(predictions_vglm$Variable)
  ind<-which(predictions_vglm$Response=="Agree")
  sorted_agree<- predictions_vglm[ind,]
  rm(ind)
  sorted_agree<-sorted_agree[order(sorted_agree$Predictions),]
  predictions_vglm$Variable<-factor(predictions_vglm$Variable, 
                                    levels = unique(sorted_agree$Variable))
  rm(sorted_agree)
  colour_pal<-brewer.pal(8, "RdYlBu")
  predictions_vglm$Significance<-as.factor(predictions_vglm$Significance) %>%
    relevel(ref = "Reference")
   shapes_code<-c(4, 1, 16)
   predictions_vglm$Variable<-fct_recode(predictions_vglm$Variable, "Yorkshire and\nthe Humber"="Yorkshire and the Humber")
  p_vglm<-ggplot(predictions_vglm, aes(x = Variable, y = Predictions,ymax = upr, ymin = lwr, colour = Response, group = Response, shape = Significance))+
    geom_pointrange(position=position_dodge(width = 0.5))+
    theme_minimal()+
    #  ylim(c(0, 0.5))+
    scale_colour_manual(values = colour_pal[c(1:3, 7:8)])+
      scale_shape_manual(values = shapes_code)+
    xlab(predictor_name)+
    ylab("Prediction probability")+
    theme(axis.text.x = element_text(angle = 25, vjust = 1, hjust=0.5), 
          plot.margin = unit(c(0.2, 1, 0.1, 0.2),                                                                        "inches"), 
          legend.position="bottom")+
    coord_cartesian(clip = 'off')+
    guides(color = "none")
  
  ind<-which(predictions_vglm$Variable==levels(predictions_vglm$Variable)[length(levels(predictions_vglm$Variable))])
  p_vglm<- p_vglm +
    annotate("text", x =(length(levels(predictions_vglm$Variable)))+0.5, 
             y = predictions_vglm$Predictions[ind], 
             label = predictions_vglm$Response[ind],
             hjust= 0, size = 3)
  return(p_vglm)
}

plot_by_predictor<-function(predictions_vglm,  predictor_name){
    predictions_vglm$Response<-fct_recode(predictions_vglm$Response,"Neither"="Neither agree nor disagree") 
    ##try this without built up
    if (length(grep("ACN grassland|Arable|Woodland|Improved grassland",predictor_name))>=1){
      cats_ord<-unique(predictions_vglm$Variable)
      str_ind<-gregexpr(" " , cats_ord[3:5])
      str_ind<-sapply(str_ind,"[[",1)
      cats_ord[3:5]<-substr(cats_ord[3:5],1, str_ind-1)
      rm(str_ind)
      ind<-c(2, 1, order(as.numeric(cats_ord[3:5]))+2)
      predictions_vglm$Variable<-as.factor(predictions_vglm$Variable)
      predictions_vglm$Variable<-factor(predictions_vglm$Variable,levels=levels( predictions_vglm$Variable)[ind])
  } else{
    predictions_vglm$Variable<-as.factor(predictions_vglm$Variable) 
  }
  colour_pal<-brewer.pal(8, "RdYlBu")
  predictions_vglm$Significance<-as.factor(predictions_vglm$Significance) %>%
    relevel(ref = "Reference")
    if (length(levels(predictions_vglm$Significance))==3){
       shapes_code<-c(4, 1, 16)
    }else {
      shapes_code<-c(4,  16)
    }
 
  p_vglm<-ggplot(predictions_vglm,
                   aes(x = Variable, y = Predictions,ymax = upr, 
                       ymin = lwr, colour = Response, 
                     shape = Significance))+
    geom_pointrange(position=position_dodge(width = 0.5))+
    theme_minimal()+
    #  ylim(c(0, 0.5))+
    scale_colour_manual(values = colour_pal[c(1:3, 7:8)])+
      scale_shape_manual(values = shapes_code)+
    xlab(predictor_name)+
    ylab("Prediction probability")+
    theme(axis.text.x = element_text(angle = 25, vjust = 1, hjust=0.5), 
           plot.margin = unit(c(0.2, 1, 0.1, 0.2),   "inches"),
          legend.position="bottom")+
    coord_cartesian(clip = 'off') +
    guides(color = "none")
  
  ind<-which(predictions_vglm$Variable==levels(predictions_vglm$Variable)[length(levels(predictions_vglm$Variable))])
  p_vglm<- p_vglm +
    annotate("text", x =(length(levels(predictions_vglm$Variable)))+0.5, 
             y = predictions_vglm$Predictions[ind], 
             label = predictions_vglm$Response[ind],
             hjust= 0, size = 3)
  return(p_vglm)
}


plot_by_numeric<-function(predictions_vglm, predictor_label){
    predictions_vglm$Response<-fct_recode(predictions_vglm$Response,"Neither"="Neither agree nor disagree") 
 colour_pal<-brewer.pal(8, "RdYlBu")
 predictions_vglm$Significance<-as.factor(predictions_vglm$Significance) %>%
   relevel(ref = "Reference")
 if (length(levels(predictions_vglm$Significance))==3){
       shapes_code<-c(4, 1, 16)
   }else {
      shapes_code<-c(4,  16)
    }
 
  p_vglm<-ggplot(predictions_vglm,
                   aes(x = Variable, y = Predictions,ymax = upr, 
                       ymin = lwr, colour = Response,fill = Response, group = Response))+
     geom_ribbon(alpha = 0.5)+
    geom_line(aes(linetype=Significance),size=0.7)+
  
  #  geom_pointrange(position=position_dodge(width = 0.5))+
    theme_minimal()+
   #    scale_shape_manual(values = shapes_code)+
    #  ylim(c(0, 0.5))+
    scale_colour_manual(values = colour_pal[c(1:3, 7:8)])+
     scale_fill_manual(values = colour_pal[c(1:3, 7:8)])+
  scale_linetype_manual(values=c("twodash", "dotted", "solid"))+
    xlab(predictor_label)+
    ylab("Prediction probability")
    #guides(color = "none")
  
 return(p_vglm)
}


```


## Plots
```{r plotting_vglms, echo = FALSE, warning = FALSE}

terms<-attr(adj_vglm@terms$terms, "term.labels")


predictor_names<-c("Region", "Home_IMD_quint", 
                   "Income", "ACNG_A_pred_ptc_wtd_percent_cats",
                   "AH_A_pred_ptc_wtd_percent_cats", 
                   "BMYW_A_pred_ptc_wtd_percent_cats",
                   "BUAG_A_pred_ptc_wtd_percent_cats",
                   "IG_A_pred_ptc_wtd_percent_cats")
predictor_labels<-c("Region", "IMD", "Income",
                    "ACN grassland", "Arable", "Woodland",
                    "Built up and gardens","Improved grassland")
pred_code<-c("Region", "IMD", "Inc",
             "ACNG", "AH", "BMYW",
             "BUAG","IG")

for (i in 1:length(predictor_names)){
  # Generate data.frame with new data for predictions
  new_data_df<-create_new_data(mod_data[[predictor_names[i]]],
                                terms, predictor_names[i])  %>%
    mutate_if(is.character,as.factor)
  
  if (predictor_names[i]!="BUAG_A_pred_ptc_wtd_percent_cats"){
    new_data_df$BUAG_A_pred_ptc_wtd_percent_cats<- ">0 - <50"
  }
  ## Predict outcome
  predictions_vglm<-predict_for_plots(new_data_df,predictor_names[i], adj_vglm, mod_data$local_good_nature_ord)
  
  ## Plot predictions
    if (predictor_names[i]=="Region"){
    p_by_pred<-plot_by_predictor_sorted(predictions_vglm, predictor_labels[i])
  }else{
     p_by_pred<-plot_by_predictor(predictions_vglm, predictor_labels[i])
  }
  assign(paste0("preds_vglm_adj_", pred_code[i]), predictions_vglm)
  assign(paste0("p_by_pred_", pred_code[i]),p_by_pred)
}

rm(i,   p_by_resp,  p_by_pred, predictions_vglm, new_data_df)

## Save all prediction plots
list_plots<-ls(pattern = "p_by_pred")
setwd(Figures_wd)
for ( i in 1:length(list_plots)){
  start_char<-max(unlist(gregexpr("_", list_plots[i])))
  ggsave(paste0("plot_preds_nature_opps_ord_by_pred", substr(list_plots[i], start_char, nchar(list_plots[i])), ".png"),plot =  plot(get(list_plots[i])),dpi = 300, height = 4.75, width = 7, units = "in")
  rm(start_char)

}

rm(i, list_plots)

## Predict good opporutnities to see nature by number of residential land covers
terms<-attr(adj_vglm_num_habs@terms$terms, "term.labels")
new_data_df<-create_new_data(mod_data$num_habs_wtd,
                                terms, "num_habs_wtd")
new_data_df$BUAG_A_pred_ptc_wtd_percent_cats<-">0 - <50"
predictions_vglm<-predict_for_plots(new_data_df,"num_habs_wtd", adj_vglm_num_habs, mod_data$local_good_nature_ord)

## Plot opportunities to see nature by number of residential land covers
p_vglm_num<-plot_by_numeric(predictions_vglm,"Number of habitats")
setwd(Figures_wd)
ggsave("RQ1_ordered_predictions_num_habitats.png", dpi = 300,width = 6, height = 4, units = "in")
p_vglm_num

rm(i, list_plots)
list_vglm<-ls(pattern = "vglm")
rm(list = list_vglm)
rm(list_vglm)
list_plots<-ls(pattern = "p_by_")
rm(list = list_plots)
rm(list_plots)
rm(adding_model_info, all_results, all_unadj, null, null_par, plot_by_predictor, plot_by_predictor_sorted, plot_by_response, predict_for_plots, terms, unadj_IMD, unadj_inc, unadj_region, terms, new_data_df,predictions_vglm, p_vglm_num, plot_by_numeric, all_results_num_habs)


```





<!---BLOCK_LANDSCAPE_START--->

# RQ2, Outcome 2 - Life satisfaction

```{r life_sati, echo = FALSE, warning = FALSE}

## Set reference level 
mod_data$M1_Q5_g<-relevel(mod_data$M1_Q5_g, ref = "Neither agree nor disagree")

RQ2_preds<-c("M1_Q5_g","M1_Q5_comp", "Nature_opp_met_bin")
RQ2_pred_names<-c("good_nature", "qual_comp", "nature_sat")

for (i in 1:length(RQ2_preds)){
  ## For each perceived green and natural space quality predictor, fit an unadjusted model predicting life satisfaction
  formula <- reformulate(RQ2_preds[i],response = "Wellbeing_sat_num")
  RQ2_unadj<-glm(formula, na.action = na.omit,
                 data = mod_data, weights = rescaled_weights)
  assign(paste0("unadj_", RQ2_pred_names[i]), RQ2_unadj)
  RQ2_unadj_tbl<-glm_tbl_regression(RQ2_unadj)
  assign(paste0("unadj_", RQ2_pred_names[i], "_tbl"),  RQ2_unadj_tbl)
  rm(RQ2_unadj,  RQ2_unadj_tbl)
  ## For each perceived green and natural space quality predictor, fit an adjusted model predicting life satisfaction
  formula <- reformulate(c(RQ2_preds[i], "Region + Home_IMD_quint + Income + Gender +  Age_Band +  Ethnicity_cats +  Marital_cats +  car_cats+ Dog + Gen_health_3cats  + Illnesses + Year +covid_restrictions  + season"),response = "Wellbeing_sat_num")
  RQ2_adj<-glm(formula, na.action = na.omit,
               data = mod_data, weights = rescaled_weights, contrasts = list(Region="contr.sum"))
  assign(paste0("adj_", RQ2_pred_names[i]), RQ2_adj)
  RQ2_adj_tbl<-glm_tbl_regression(RQ2_adj)
  assign(paste0("adj_", RQ2_pred_names[i], "_tbl"),  RQ2_adj_tbl)
  rm(RQ2_adj,  RQ2_adj_tbl)
}

rm(formula, i)

## Merge all results tables
t_merge<-tbl_merge(tbls = list(unadj_good_nature_tbl,adj_good_nature_tbl,unadj_qual_comp_tbl,adj_qual_comp_tbl,unadj_nature_sat_tbl,adj_nature_sat_tbl), tab_spanner = c("Unadj - Nature opps", "Adj - Nature opps", "Unadj - comp", "Adj - Comp" ,"Unadj - Sat", "Adj- Sat")) %>%
modify_table_body(~.x %>% arrange(row_type="glance_statistic")) %>%
  as_flex_table() 
## print model results table
t_merge   

rm(list =ls(pattern = "adj.*_tbl"))
rm(list =ls(pattern = "unadj"))
rm(t_merge)
```

<!---BLOCK_LANDSCAPE_STOP--->

```{r plot_models_RQ2_outcome1, echo = FALSE}

## For each perceived green and natural space quality indicator, find the ajdusted models from the environment
mod_list<-ls(pattern= "adj_")
mod_list<-mod_list[c(1, 3, 2)]

## For each perceived green and natural space quality predictor, tidy the model output and add confidence intervals for the purposes of plotting
for (i in 1:length(mod_list)){
  mod_obj<-get(mod_list[i])
  ## Tidy the model output
  tidy_mod<-tidy( mod_obj) %>%
  as.data.frame()%>%
  mutate(Variable =RQ2_pred_names[i])
  ## Add confidence intervals
  confint_mod<-confint(mod_obj) %>%
  as.data.frame() %>%
  mutate(Variable =RQ2_pred_names[i])
  confint_mod$term<-tidy_mod$term
  tidy_mod<-merge(tidy_mod, confint_mod)
  rm(confint_mod)
  assign(paste0("tidy_",mod_list[i] ), tidy_mod)
  rm(tidy_mod, mod_obj)
}

rm(i, mod_list)
## Bind together all tidied adjusted model outputs
tidy_mod_list<-ls(pattern = "tidy_adj")
all_tidy_mods <- do.call(rbind, mget(tidy_mod_list))
rm(list = tidy_mod_list)
rm(tidy_mod_list)

names(all_tidy_mods)[7:8]<-c("lwr", "upr")

## Select only rows associated with each key predictor
ind<-grep("M1_Q5_.*|Nature_opp_met_bin", all_tidy_mods$term)
all_tidy_mods<-all_tidy_mods[ind,]
all_tidy_mods$term<-gsub("M1_Q5_g", "",all_tidy_mods$term)
all_tidy_mods$term<-gsub("Nature_opp_met_bin","", all_tidy_mods$term)

## Add significance categories to data.frame for plotting purposes
ind<-which(all_tidy_mods$p.value<0.05)
all_tidy_mods$Significance<-"Not significant"
all_tidy_mods$Significance[ind]<-"Significant"
all_tidy_mods$term<-as.character(all_tidy_mods$term)
all_tidy_mods$term[6]<-"Quality composite"
all_tidy_mods$term<-as.factor(all_tidy_mods$term)
all_tidy_mods$term<-factor(all_tidy_mods$term, levels = c("Strongly disagree", "Disagree", "Agree", "Strongly agree", "Satisfied","Quality composite"))

## Add facet labels to data.frame for plotting purposes
term=c("good_nature", "qual_comp", "nature_sat")
facet_labels<-c("Good nature\nopportunities","Quality\ncomposite","Nearby\nnature\nsatisfaction")
facet_names_df<- data.frame(term, facet_labels)
rm(term, facet_labels)
ind<-match(all_tidy_mods$Variable,facet_names_df$term)
all_tidy_mods$facet_labels<-facet_names_df$facet_labels[ind]
rm(ind, facet_names_df)

all_tidy_mods$facet_labels<-as.factor(all_tidy_mods$facet_labels)
all_tidy_mods$facet_labels<-factor(all_tidy_mods$facet_labels, levels = c("Good nature\nopportunities"  , "Quality\ncomposite", "Nearby\nnature\nsatisfaction"))

## Plot coefficients associated with eahc predictor on the same plot
p<-ggplot(all_tidy_mods, aes(x = term, y = estimate, ymin = lwr, ymax = upr))+
  geom_pointrange(aes(shape = Significance))+
  theme_minimal()+
  facet_grid(rows = vars(facet_labels), drop = TRUE, scales = "free_y",space = "free")+
  coord_flip()+
  ylab("Beta coefficient")+
  geom_hline(yintercept=0 ,linetype="dashed")+
  xlab("")
  
## Save figure
p
setwd(Figures_wd)
ggsave("RQ2_coefs_life_sat_adj.png", dpi = 300, height = 4, width = 6)

rm(p, all_tidy_mods)
```



<!---BLOCK_LANDSCAPE_START--->
# RQ2, Outcome 2 - Visit frequency

```{r visit_freq, echo = FALSE, warning = FALSE}

## Set reference levle of outcome
mod_data$visit_freq_bin<-relevel(mod_data$visit_freq_bin, ref = "<1 a week")

for (i in 1:length(RQ2_preds)){
  ## For each perceived green and natural space quality predictor fit an unadjusted model predicting visit frequency as a binary outcome
  formula <- reformulate(RQ2_preds[i],response = "visit_freq_bin")
  RQ2_unadj<-glm(formula, na.action = na.omit,
                 data = mod_data, weights = rescaled_weights, family = "binomial")
  assign(paste0("unadj_", RQ2_pred_names[i]), RQ2_unadj)
  ## Generate summary table with custom function
  RQ2_unadj_tbl<-bin_tbl_regression(RQ2_unadj)
  assign(paste0("unadj_", RQ2_pred_names[i], "_tbl"),  RQ2_unadj_tbl)
  rm(RQ2_unadj,  RQ2_unadj_tbl)
  
    ## For each perceived green and natural space quality predictor fit an adjusted model predicting visit frequency as a binary outcome
  formula <- reformulate(c(RQ2_preds[i], "Region + Home_IMD_quint + Income + Gender +  Age_Band +  Ethnicity_cats +  Marital_cats +  car_cats+ Dog +  Gen_health_3cats  + Illnesses + Year +covid_restrictions + season"),response = "visit_freq_bin")
  RQ2_adj<-glm(formula, na.action = na.omit,
               data = mod_data, weights = rescaled_weights, contrasts = list(Region="contr.sum"), family = "binomial")
  assign(paste0("adj_", RQ2_pred_names[i]), RQ2_adj)
  ## Produce summary table with custom function
  RQ2_adj_tbl<-bin_tbl_regression(RQ2_adj)
  assign(paste0("adj_", RQ2_pred_names[i], "_tbl"),  RQ2_adj_tbl)
  rm(RQ2_adj,  RQ2_adj_tbl)
}

rm(formula, i)

## Merge all unadjusted and adjusted model tables
t_merge<-tbl_merge(tbls = list(unadj_good_nature_tbl,adj_good_nature_tbl,unadj_qual_comp_tbl,adj_qual_comp_tbl,unadj_nature_sat_tbl,adj_nature_sat_tbl), tab_spanner = c("Unadj - Nature opps", "Adj - Nature opps", "Unadj - comp", "Adj - Comp" ,"Unadj - Sat", "Adj- Sat")) %>%
modify_table_body(~.x %>% arrange(row_type="glance_statistic")) %>%
  as_flex_table() 
## print model summary table
t_merge   

rm(list =ls(pattern = "adj.*_tbl"))
rm(list =ls(pattern = "unadj"))
rm(t_merge)

```

<!---BLOCK_LANDSCAPE_STOP--->

```{r plot_models_RQ2_visit_freq, echo = FALSE, warning = FALSE}


## Get adjusted model objects
mod_list<-ls(pattern= "adj_")
mod_list<-mod_list[c(1, 3, 2)]
for (i in 1:length(mod_list)){
  mod_obj<-get(mod_list[i])
  ## Tidy model object
  tidy_mod<-tidy( mod_obj) %>%
  as.data.frame()%>%
    ## Add odds ratios
  mutate(Variable =RQ2_pred_names[i]) %>%
    mutate(OR = exp(estimate))
  ## Calculate odds ratio confidence intervals
  confint_mod<-exp(confint(mod_obj)) %>%
  as.data.frame() %>%
  mutate(Variable =RQ2_pred_names[i])
  confint_mod$term<-tidy_mod$term
  ## Merge tidy model results and confidence intervals
  tidy_mod<-merge(tidy_mod, confint_mod)
  rm(confint_mod)
  assign(paste0("tidy_",mod_list[i] ), tidy_mod)
  rm(tidy_mod, mod_obj)
}

rm(i, mod_list)
tidy_mod_list<-ls(pattern = "tidy_adj")
## Merge together all tidied adjusted model results tables
all_tidy_mods <- do.call(rbind, mget(tidy_mod_list))
rm(list = tidy_mod_list)
rm(tidy_mod_list)

names(all_tidy_mods)[8:9]<-c("lwr", "upr")

ind<-grep("M1_Q5_.*|Nature_opp_met_bin", all_tidy_mods$term)
all_tidy_mods<-all_tidy_mods[ind,]
all_tidy_mods$term<-gsub("M1_Q5_g", "",all_tidy_mods$term)
all_tidy_mods$term<-gsub("Nature_opp_met_bin","", all_tidy_mods$term)

## Add significance information to model results table
ind<-which(all_tidy_mods$p.value<0.05)
all_tidy_mods$Significance<-"Not significant"
all_tidy_mods$Significance[ind]<-"Significant"

## Setting up information for plotting
all_tidy_mods$term<-as.character(all_tidy_mods$term)
all_tidy_mods$term[6]<-"Quality composite"
all_tidy_mods$term<-as.factor(all_tidy_mods$term)
all_tidy_mods$term<-factor(all_tidy_mods$term, levels = c("Strongly disagree", "Disagree", "Agree", "Strongly agree", "Satisfied","Quality composite"))
term=c("good_nature", "qual_comp", "nature_sat")
facet_labels<-c("Good nature\nopportunities","Quality\ncomposite","Nearby\nnature\nsatisfaction")
facet_names_df<- data.frame(term, facet_labels)
rm(term, facet_labels)
ind<-match(all_tidy_mods$Variable,facet_names_df$term)
all_tidy_mods$facet_labels<-facet_names_df$facet_labels[ind]
rm(ind, facet_names_df)

all_tidy_mods$facet_labels<-as.factor(all_tidy_mods$facet_labels)
all_tidy_mods$facet_labels<-factor(all_tidy_mods$facet_labels, levels = c("Good nature\nopportunities"  , "Quality\ncomposite", "Nearby\nnature\nsatisfaction"))

p<-ggplot(all_tidy_mods, aes(x = term, y = OR, ymin = lwr, ymax = upr))+
  geom_pointrange(aes(shape = Significance))+
  scale_shape_manual(values=c(1, 19))+
  theme_minimal()+
  facet_grid(rows = vars(facet_labels), drop = TRUE, scales = "free_y",space = "free")+
  coord_flip()+
  ylab("Odds Ratio")+
  geom_hline(yintercept=1 ,linetype="dashed")+
  xlab("")
  
p
setwd(Figures_wd)
ggsave("RQ2_OR_visit_freq_adj.png", dpi = 300, height = 4, width = 6)

rm(p, all_tidy_mods, adj_good_nature, adj_nature_sat, adj_qual_comp, all_results_num_habs)
```


```{r sem, echo = FALSE, eval = FALSE}

## convert variables to ordered factors so they can be easily converted to numeric
pans_data$Home_IMD_quint_ord<-ordered(pans_data$Home_IMD_quint)
pans_data$Home_IMD_quint_num<-as.numeric(pans_data$Home_IMD_quint_ord)

pans_data$income_ord<-ordered(pans_data$Income)
pans_data$income_num<-as.numeric(pans_data$income_ord)

pans_data$visit_freq_bin_ord<-ordered(pans_data$visit_freq_bin)
pans_data$visit_freq_bin_num<-as.numeric(pans_data$visit_freq_bin_ord)-1

## Create dummy variables for categorial variables
region_dummies<-dummy_cols(pans_data$Region)[,2:10]
names(region_dummies)<-gsub(".data_", "", names(region_dummies))
names(region_dummies)<-gsub(" ", "_", names(region_dummies))
pans_data<-cbind(pans_data, region_dummies)

age_dummies<-dummy_cols(pans_data$Age_Band)[,2:6]
names(age_dummies)<-gsub(".data_", "a", names(age_dummies))
names(age_dummies)<-gsub("-", "_", names(age_dummies))
names(age_dummies)<-gsub("\\+", "", names(age_dummies))
pans_data<-cbind(pans_data, age_dummies)
rm(region_dummies, age_dummies)

year_dummies<-dummy_cols(pans_data$Year)[,2:5]
names(year_dummies)<-gsub(".data_", "Y", names(year_dummies))
pans_data<-cbind(pans_data,year_dummies)
rm(year_dummies)

covid_dummies<-dummy_cols(pans_data$covid_restrictions)[,2:5]
names(covid_dummies)<-gsub(".data_", "", names(covid_dummies))
names(covid_dummies)<-gsub(" ", "_", names(covid_dummies))
pans_data<-cbind(pans_data,covid_dummies)
rm(covid_dummies)

## Sort factor levels and convert to numeric where necessary
pans_data$Gender_2levs<-factor(pans_data$Gender, levels = c("Female", "Male"))

pans_data$Gen_health_3cats<-factor(pans_data$Gen_health_3cats, levels = c("Bad","Fair","Good"))
pans_data$Gen_health_3cats_ord<-ordered(pans_data$Gen_health_3cats)
pans_data$Gen_health_3cats_num<-as.numeric(pans_data$Gen_health_3cats_ord)

qual_model <- '
# latent variable
Green_space_quality =~ M1_Q5_a_ord + M1_Q5_b_ord + M1_Q5_c_ord + M1_Q5_d_ord + M1_Q5_e_ord + M1_Q5_f_ord + M1_Q5_g_ord

# Regressions
## south east excluded from region, 16 - 24 excluded from age, 2020 excluded from year, no restrictions excluded from covid restrictions

visit_freq_bin_num ~ Green_space_quality + Home_IMD_quint_num + income_num + East + East_Midlands + London + North_East + North_West + South_West + West_Midlands + Yorkshire_and_the_Humber + Gender_2levs  + a25_39 + a40_54 + a55_64 + a65 + Ethnicity_cats + Marital_cats + car_cats + Gen_health_3cats_ord + Illnesses + Y2021 + Y2022 + Minimal_restrictions + Outdoor_recreation_limited + First_full_lockdown

Wellbeing_sat_num ~ Green_space_quality + visit_freq_bin_num + Home_IMD_quint_num + income_num + East + East_Midlands + London + North_East + North_West + South_West + West_Midlands + Yorkshire_and_the_Humber + Gender_2levs + a25_39 + a40_54 + a55_64 + a65 + Ethnicity_cats + Marital_cats + car_cats + Gen_health_3cats_ord + Illnesses + Y2021 + Y2022  + Minimal_restrictions + Outdoor_recreation_limited + First_full_lockdown

Green_space_quality ~ Home_IMD_quint_num + income_num + + East + East_Midlands + London + North_East + North_West + South_West + West_Midlands + Yorkshire_and_the_Humber + Gender_2levs + a25_39 + a40_54 + a55_64 + a65 + Ethnicity_cats + Marital_cats + car_cats + Gen_health_3cats_ord + Illnesses + Y2021 + Y2022  + Minimal_restrictions + Outdoor_recreation_limited + First_full_lockdown
'

fit <- sem(qual_model, data = mod_data[no_missing_ind_gender,])

setwd(Results_wd)
## Create standardised coefficients table
## Presented in supp mats
tidy_fit_stand<-standardizedSolution(fit) 

## There are hundreds of rows, so only included key rows
ind<-grep("Green_space_quality|visit_freq_bin_num|Wellbeing_sat_num", tidy_fit_stand$lhs)
tidy_fit_stand<-tidy_fit_stand[ind,]
rm(ind)
tidy_fit_stand<-pivot_wider(tidy_fit_stand,id_cols = rhs, names_from = lhs, values_from = c( est.std,se, pvalue, ci.lower, ci.upper))

cols_green<-grep("Green", names(tidy_fit_stand))
cols_sat<-grep("Wellbeing", names(tidy_fit_stand))
cols_visit<-grep("visit", names(tidy_fit_stand))
tidy_fit_stand<-tidy_fit_stand[, c(1, cols_green, cols_visit, cols_sat)]
rm(cols_green, cols_visit, cols_sat)

tidy_fit_stand[,2:NCOL(tidy_fit_stand)]<-round(tidy_fit_stand[,2:NCOL(tidy_fit_stand)], digits =3)

col_ind<-grep("pvalue", names(tidy_fit_stand))
tidy_fit_stand$est.stars_Green_space_quality<-round(tidy_fit_stand$est.std_Green_space_quality, digits =2)
tidy_fit_stand$est.stars_visit_freq_bin_num<-round(tidy_fit_stand$est.std_visit_freq_bin_num, digits =2)
tidy_fit_stand$est.stars_Wellbeing_sat_num<-round(tidy_fit_stand$est.std_Wellbeing_sat_num, digits =2)

stars_ind<-grep("stars", names(tidy_fit_stand))
stars_names<-names(tidy_fit_stand)[stars_ind]
for (i in 1:length(col_ind)){
  ind<-which(tidy_fit_stand[col_ind[i]]<0.001)
  tidy_fit_stand[[stars_names[i]]][ind]<-paste0( tidy_fit_stand[[stars_names[i]]][ind], "***")
  ind<-which(tidy_fit_stand[col_ind[i]]<0.01 & tidy_fit_stand[col_ind[i]]>=0.001)
   tidy_fit_stand[[stars_names[i]]][ind]<-paste0( tidy_fit_stand[[stars_names[i]]][ind],"**")
  ind<-which(tidy_fit_stand[col_ind[i]]<0.05 & tidy_fit_stand[col_ind[i]]>=0.01)
   tidy_fit_stand[[stars_names[i]]][ind]<-paste0( tidy_fit_stand[[stars_names[i]]][ind], "*")
}

rm(i, col_ind, stars_ind, stars_names)
tidy_fit_stand<-tidy_fit_stand[,c(1:2, 17, 3:7, 18, 8:12, 19, 13:16)]

write.csv(tidy_fit_stand, "tidy_sem_results_standardised.csv")

tidy_fit_stand_flex<-flextable(tidy_fit_stand)
tidy_fit_stand_flex

rm(tidy_fit_stand, tidy_fit_stand_flex)

### Prepare unstandardised results table, presented in main manuscript
tidy_fit<-tidySEM::table_results(fit , digits = 3)
ind<-grep("M1_Q5_comp|visit_freq_bin_num|Wellbeing_sat_num", tidy_fit$label)
tidy_fit<-tidy_fit[ind,]
rm(ind)
ind<-grep("Variances|Means", tidy_fit$label)
tidy_fit<-tidy_fit[-ind,]
rm(ind)

tidy_fit$Predictor<-NA
tidy_fit$Outcome<-NA
for (i in 1:NROW(tidy_fit)){
  end_char<-unlist(gregexpr(pattern ='\\.',tidy_fit$label[i]))[[1]]
  tidy_fit$Outcome[i]<-substr(tidy_fit$label[i], 1, end_char-1)
  rm(end_char)
  start_char<-unlist(gregexpr(pattern ='\\.',tidy_fit$label[i]))[[2]]
  tidy_fit$Predictor[i]<-substr(tidy_fit$label[i], start_char+1, nchar(tidy_fit$label[i]))
  rm(start_char)
}


tidy_fit<-pivot_wider(tidy_fit,id_cols = Predictor, names_from = Outcome, values_from = c( est_sig,se, pval,confint))

cols_green<-grep("Green", names(tidy_fit))
cols_sat<-grep("Wellbeing", names(tidy_fit))
cols_visit<-grep("visit", names(tidy_fit))
tidy_fit<-tidy_fit[, c(1, cols_green, cols_visit, cols_sat)]
rm(cols_green, cols_visit, cols_sat)

tidy_fit_flex<-flextable(tidy_fit) %>%
  colformat_num(j = c("pval_Green_space_quality", "pval_visit_freq_bin_num",   "pval_Wellbeing_sat_num"  ), digits = 3)
## print table
tidy_fit_flex

## save table
setwd(Results_wd)
write.csv(tidy_fit, "tidy_sem_results_unstandardised.csv")
rm(tidy_fit, tidy_fit_flex)

#summary(fit, standardized=TRUE, fit.measures=TRUE)
#fitMeasures(fit, standardized=TRUE)
#modindices(fit,sort=TRUE)

## plot standardised results
## This plot is too complicated though as it includes all variables
## I did it manually in the paper
p<-lavaanPlot(fit, coefs = TRUE, sig = 0.05, stand = TRUE, stars = "regress")

p
rm(p)
## https://cran.r-project.org/web/packages/lavaanPlot/vignettes/Intro_to_lavaanPlot.html
```

## Structural equation models
### By different land covers
```{r sem_green_comp, echo = FALSE}

## convert variables to ordered factors so they can be easily converted to numeric
mod_data$Home_IMD_quint_ord<-ordered(mod_data$Home_IMD_quint)
mod_data$Home_IMD_quint_num<-as.numeric(mod_data$Home_IMD_quint_ord)

mod_data$income_ord<-ordered(mod_data$Income)
mod_data$income_num<-as.numeric(mod_data$income_ord)

mod_data$visit_freq_bin<-relevel(mod_data$visit_freq_bin, ref = "<1 a week")
mod_data$visit_freq_bin_ord<-ordered(mod_data$visit_freq_bin)
mod_data$visit_freq_bin_num<-as.numeric(mod_data$visit_freq_bin_ord)-1

## Create dummy variables for categorial variables
region_dummies<-dummy_cols(mod_data$Region)[,2:10]
names(region_dummies)<-gsub(".data_", "", names(region_dummies))
names(region_dummies)<-gsub(" ", "_", names(region_dummies))
mod_data<-cbind(mod_data, region_dummies)

age_dummies<-dummy_cols(mod_data$Age_Band)[,2:6]
names(age_dummies)<-gsub(".data_", "a", names(age_dummies))
names(age_dummies)<-gsub("-", "_", names(age_dummies))
names(age_dummies)<-gsub("\\+", "", names(age_dummies))
mod_data<-cbind(mod_data, age_dummies)
rm(region_dummies, age_dummies)

year_dummies<-dummy_cols(mod_data$Year)[,2:5]
names(year_dummies)<-gsub(".data_", "Y", names(year_dummies))
mod_data<-cbind(mod_data,year_dummies)
rm(year_dummies)

covid_dummies<-dummy_cols(mod_data$covid_restrictions)[,2:5]
names(covid_dummies)<-gsub(".data_", "", names(covid_dummies))
names(covid_dummies)<-gsub(" ", "_", names(covid_dummies))
mod_data<-cbind(mod_data,covid_dummies)
rm(covid_dummies)

season_dummies<-dummy_cols(mod_data$season)[,2:5]
names(season_dummies)<-gsub(".data_", "", names(season_dummies))
names(season_dummies)<-gsub(" ", "_", names(season_dummies))
mod_data<-cbind(mod_data,season_dummies)
rm(season_dummies)

## Sort factor levels and convert to numeric where necessary
mod_data$Gender_2levs<-factor(mod_data$Gender, levels = c("Female", "Male"))

mod_data$Gen_health_3cats<-factor(mod_data$Gen_health_3cats, levels = c("Bad","Fair","Good"))
mod_data$Gen_health_3cats_ord<-ordered(mod_data$Gen_health_3cats)
mod_data$Gen_health_3cats_num<-as.numeric(mod_data$Gen_health_3cats_ord)

mod_data$ACNG_cats_ord<-ordered(mod_data$ACNG_A_pred_ptc_wtd_percent_cats)
mod_data$ACNG_cats_num<-as.numeric(mod_data$ACNG_cats_ord)

mod_data$AH_cats_ord<-ordered(mod_data$AH_A_pred_ptc_wtd_percent_cats)
mod_data$AH_cats_num<-as.numeric(mod_data$AH_cats_ord)

mod_data$BMYW_cats_ord<-ordered(mod_data$BMYW_A_pred_ptc_wtd_percent_cats)
mod_data$BMYW_cats_num<-as.numeric(mod_data$BMYW_cats_ord)

mod_data$BUAG_cats_ord<-ordered(mod_data$BUAG_A_pred_ptc_wtd_percent_cats)
mod_data$BUAG_cats_num<-as.numeric(mod_data$BUAG_cats_ord)

mod_data$IG_cats_ord<-ordered(mod_data$IG_A_pred_ptc_wtd_percent_cats)
mod_data$IG_cats_num<-as.numeric(mod_data$IG_cats_ord)

## Specify model
model_spec <- ' 
# direct effect
             Wellbeing_sat_num ~1+ b2*M1_Q5_comp + b1*visit_freq_bin_num + c1*ACNG_cats_num + c2*AH_cats_num + c3*BMYW_cats_num + c4*BUAG_cats_num + c5*IG_cats_num + Home_IMD_quint_num + income_num + East + East_Midlands + London + North_East + North_West + South_West + West_Midlands + Yorkshire_and_the_Humber + Gender_2levs + a16_24 + a25_39 + a55_64 + a65 + Ethnicity_cats + Marital_cats + car_cats + Dog + Gen_health_3cats_num + Illnesses + Y2021 + Y2022 + Y2023 + Minimal_restrictions + Outdoor_recreation_limited + First_full_lockdown + Spring + Summer + Autumn
             
           # mediators
  
            M1_Q5_comp ~1+ h1q*ACNG_cats_num + h2q*AH_cats_num + h3q*BMYW_cats_num + h4q*BUAG_cats_num + h5q*IG_cats_num + Home_IMD_quint_num + income_num + East + East_Midlands + London + North_East + North_West + South_West + West_Midlands + Yorkshire_and_the_Humber + Gender_2levs +  a16_24 + a25_39 + a55_64 + a65+ Ethnicity_cats + Marital_cats + car_cats + Dog + Gen_health_3cats_num + Illnesses + Y2021 + Y2022 + Y2023  + Minimal_restrictions + Outdoor_recreation_limited + First_full_lockdown + Spring + Summer + Autumn
            
             visit_freq_bin_num ~ 1+ d*M1_Q5_comp + h1v*ACNG_cats_num + h2v*AH_cats_num + h3v*BMYW_cats_num + h4v*BUAG_cats_num + h5v*IG_cats_num + Home_IMD_quint_num + income_num + East + East_Midlands + London + North_East + North_West + South_West + West_Midlands + Yorkshire_and_the_Humber + Gender_2levs  +  a16_24 + a25_39 + a55_64 + a65 + Ethnicity_cats + Marital_cats + car_cats + Dog + Gen_health_3cats_num + Illnesses + Y2021 + Y2022 + Y2023 + Minimal_restrictions + Outdoor_recreation_limited + First_full_lockdown + Spring + Summer + Autumn

            
           # indirect effects (a*b)
           
             h1vb1 := h1v*b1
             h2vb1 := h2v*b1
             h3vb1 := h3v*b1
             h4vb1 := h4v*b1
             h5vb1 := h5v*b1
             
             h1qb2 := h1q*b2
             h2qb2 := h2q*b2
             h3qb2 := h3q*b2
             h4qb2 := h4q*b2
             h5qb2 := h5q*b2
             
             h1qdb1 := h1q*d*b1
             h2qdb1 := h2q*d*b1
             h3qdb1 := h3q*d*b1
             h4qdb1 := h4q*d*b1
             h5qdb1 := h5q*d*b1
             
             ## All indirect
             ttl_indirect_h1 := (h1v*b1) + (h1q*b2) + (h1q*d*b1)
             ttl_indirect_h2 := (h2v*b1) + (h2q*b2) + (h2q*d*b1)
             ttl_indirect_h3 := (h3v*b1) + (h3q*b2) + (h3q*d*b1)
             ttl_indirect_h4 := (h4v*b1) + (h4q*b2) + (h4q*d*b1)
             ttl_indirect_h5 := (h5v*b1) + (h5q*b2) + (h5q*d*b1)
             
             
           # total effects
             totalh1 := (h1v*b1) + (h1q*b2) + (h1q*d*b1) + c1
             totalh2 := (h2v*b1) + (h2q*b2) + (h2q*d*b1) + c2
             totalh3 := (h3v*b1) + (h3q*b2) + (h3q*d*b1) + c3
             totalh4 := (h4v*b1) + (h4q*b2) + (h4q*d*b1) + c4
             totalh5 := (h5v*b1) + (h5q*b2) + (h5q*d*b1) + c5
         '

## Fit SEM
fit <- sem(model_spec, data = mod_data,sampling.weights  = "rescaled_weights")

setwd(Results_wd)
## Create standardised coefficients table
## Presented in supp mats
tidy_fit_stand<-standardizedSolution(fit)

ind<-which(tidy_fit_stand$op== ":=")
pathways<-tidy_fit_stand[ind,] 

col_ind<-grep("pvalue", names(pathways))
pathways$est_stars<-round(pathways$est.std, digits =3)
## Add stars to indicate significance
stars_ind<-grep("stars", names(pathways))
stars_names<-names(pathways)[stars_ind]
for (i in 1:length(col_ind)){
  ind<-which(pathways[col_ind[i]]<0.001)
  pathways[[stars_names[i]]][ind]<-paste0( pathways[[stars_names[i]]][ind], "***")
  ind<-which(pathways[col_ind[i]]<0.01 & pathways[col_ind[i]]>=0.001)
  pathways[[stars_names[i]]][ind]<-paste0( pathways[[stars_names[i]]][ind],"**")
  ind<-which(pathways[col_ind[i]]<0.05 & pathways[col_ind[i]]>=0.01)
  pathways[[stars_names[i]]][ind]<-paste0( pathways[[stars_names[i]]][ind], "*")
}

rm(ind, i, stars_names, stars_ind)

pathways<- pathways %>%
  mutate(conf_int=paste0(round(ci.lower, digits = 3), ",",round(ci.upper, digits = 3))) %>%
  select(rhs,est_stars, conf_int)

setwd(Results_wd)
write.csv(pathways, "tidy_sem_pathways_standardised.csv")
pathways_flex<-flextable(pathways)
print("Standardised pathways - different land covers")
pathways_flex
rm(pathways, pathways_flex)

## There are hundreds of rows, so only included key rows
ind<-grep("M1_Q5_comp|visit_freq_bin_num|Wellbeing_sat_num", tidy_fit_stand$lhs)
tidy_fit_stand<-tidy_fit_stand[ind,]
rm(ind)
tidy_fit_stand<-pivot_wider(tidy_fit_stand,id_cols = rhs, names_from = lhs, values_from = c( est.std,se, pvalue, ci.lower, ci.upper))

## Select relevant columns
cols_green<-grep("M1_Q5_comp", names(tidy_fit_stand))
cols_sat<-grep("Wellbeing", names(tidy_fit_stand))
cols_visit<-grep("visit", names(tidy_fit_stand))
tidy_fit_stand<-tidy_fit_stand[, c(1, cols_green, cols_visit, cols_sat)]
rm(cols_green, cols_visit, cols_sat)

tidy_fit_stand[,2:NCOL(tidy_fit_stand)]<-round(tidy_fit_stand[,2:NCOL(tidy_fit_stand)], digits =3)

col_ind<-grep("pvalue", names(tidy_fit_stand))
tidy_fit_stand$est.stars_Green_space_quality<-round(tidy_fit_stand$est.std_M1_Q5_comp, digits =2)
tidy_fit_stand$est.stars_visit_freq_bin_num<-round(tidy_fit_stand$est.std_visit_freq_bin_num, digits =2)
tidy_fit_stand$est.stars_Wellbeing_sat_num<-round(tidy_fit_stand$est.std_Wellbeing_sat_num, digits =2)
## Add stars to indicate significance
stars_ind<-grep("stars", names(tidy_fit_stand))
stars_names<-names(tidy_fit_stand)[stars_ind]
for (i in 1:length(col_ind)){
  ind<-which(tidy_fit_stand[col_ind[i]]<0.001)
  tidy_fit_stand[[stars_names[i]]][ind]<-paste0( tidy_fit_stand[[stars_names[i]]][ind], "***")
  ind<-which(tidy_fit_stand[col_ind[i]]<0.01 & tidy_fit_stand[col_ind[i]]>=0.001)
   tidy_fit_stand[[stars_names[i]]][ind]<-paste0( tidy_fit_stand[[stars_names[i]]][ind],"**")
  ind<-which(tidy_fit_stand[col_ind[i]]<0.05 & tidy_fit_stand[col_ind[i]]>=0.01)
   tidy_fit_stand[[stars_names[i]]][ind]<-paste0( tidy_fit_stand[[stars_names[i]]][ind], "*")
}

rm(i, col_ind, stars_ind, stars_names)
tidy_fit_stand<-tidy_fit_stand[,c(1:2, 17, 3:7, 18, 8:12, 19, 13:16)]

write.csv(tidy_fit_stand, "tidy_sem_results_standardised.csv")

tidy_fit_stand_flex<-flextable(tidy_fit_stand)
# print standardised SEM model results table
print("standardised SEM model results table")
tidy_fit_stand_flex

rm(tidy_fit_stand_flex)


fit_stats <- summary(fit, standardized = TRUE, fit.measures = TRUE)$fit
wanted <- c("chisq", "df", "cfi", "tli", "ntotal", "rmsea")
fit_stats_selected <- fit_stats[wanted]
print("Fit measures for standardised SEM")
fit_stats_selected
rm(fit_stats, wanted, fit_stats_selected)

### Prepare unstandardised results table, presented in main manuscript
sum_sem<-summary(fit)
ind<-which(sum_sem$pe$lhs=="h1vb1")
unstandard_indirect<-sum_sem$pe[ind:NROW(sum_sem$pe),] 
unstandard_indirect[,6:9]<-round(unstandard_indirect[,6:9], digits = 3)
write.csv(unstandard_indirect, "unstandardised_indirect_totals.csv")
rm(sum_sem, ind, unstandard_indirect)

tidy_fit<-tidySEM::table_results(fit , digits = 3)
ind<-grep("M1_Q5_comp|visit_freq_bin_num|Wellbeing_sat_num", tidy_fit$label)
tidy_fit<-tidy_fit[ind,]
rm(ind)
ind<-grep("Variances|Means", tidy_fit$label)
tidy_fit<-tidy_fit[-ind,]
rm(ind)

tidy_fit$Predictor<-NA
tidy_fit$Outcome<-NA
for (i in 1:NROW(tidy_fit)){
  end_char<-unlist(gregexpr(pattern ='\\.',tidy_fit$label[i]))[[1]]
  tidy_fit$Outcome[i]<-substr(tidy_fit$label[i], 1, end_char-1)
  rm(end_char)
  start_char<-unlist(gregexpr(pattern ='\\.',tidy_fit$label[i]))[[2]]
  tidy_fit$Predictor[i]<-substr(tidy_fit$label[i], start_char+1, nchar(tidy_fit$label[i]))
  rm(start_char)
}
tidy_fit$label<-NULL

class(tidy_fit$Outcome)
tidy_fit$Outcome<-gsub("M1_Q5_comp", "Green_qual_comp", tidy_fit$Outcome)

tidy_fit<-pivot_wider(tidy_fit,id_cols = Predictor, names_from = Outcome, values_from = c( est_sig,se, pval,confint))

cols_green<-grep("Green", names(tidy_fit))
cols_sat<-grep("Wellbeing", names(tidy_fit))
cols_visit<-grep("visit", names(tidy_fit))
tidy_fit<-tidy_fit[, c(1, cols_green, cols_visit, cols_sat)]
rm(cols_green, cols_visit, cols_sat)

tidy_fit_flex<-flextable(tidy_fit) %>%
  colformat_num(j = c( "pval_Green_qual_comp", "pval_visit_freq_bin_num",   "pval_Wellbeing_sat_num"  ), digits = 3)
## print table
print("Understandardised SEM results table by land covers")
tidy_fit_flex

## save table
setwd(Results_wd)
write.csv(tidy_fit, "tidy_sem_results_unstandardised.csv")
rm(tidy_fit, tidy_fit_flex)


fit_stats <- summary(fit,fit.measures = TRUE)$fit
wanted <- c("chisq", "df", "cfi", "tli", "ntotal", "rmsea")
fit_stats_selected <- fit_stats[wanted]
print("Fit measures for unstandardised SEM")
fit_stats_selected
rm(fit_stats, wanted, fit_stats_selected)




```

```{r plot_sem, echo = FALSE, eval = FALSE}
# Create the edges with labels dynamically
edges <- glue("
  tab3 -> tab2 [label = '{tidy_fit_stand[ind[3], 3]}']
  tab4 -> tab2 [label = '{tidy_fit_stand[ind[4], 3]}']
  tab5 -> tab2 [label = '{tidy_fit_stand[ind[5], 3]}']
  tab6 -> tab2 [label = '{tidy_fit_stand[ind[6], 3]}']
  tab7 -> tab2 [label = '{tidy_fit_stand[ind[7], 3]}']
  
  tab2 -> tab8 [label = '{tidy_fit_stand[ind[2], 9]}']
  tab3 -> tab8 [label = '{tidy_fit_stand[ind[3], 9]}']
  tab4 -> tab8 [label = '{tidy_fit_stand[ind[4], 9]}']
  tab5 -> tab8 [label = '{tidy_fit_stand[ind[5], 9]}']
  tab6 -> tab8 [label = '{tidy_fit_stand[ind[6], 9]}']
  tab7 -> tab8 [label = '{tidy_fit_stand[ind[7], 9]}']
  
  tab2 -> tab1 [label = '{tidy_fit_stand[ind[2], 15]}']
  tab3 -> tab1 [label = '{tidy_fit_stand[ind[3], 15]}']
  tab4 -> tab1 [label = '{tidy_fit_stand[ind[4], 15]}']
  tab5 -> tab1 [label = '{tidy_fit_stand[ind[5], 15]}']
  tab6 -> tab1 [label = '{tidy_fit_stand[ind[6], 15]}']
  tab7 -> tab1 [label = '{tidy_fit_stand[ind[7], 15]}']
  tab8 -> tab1 [label = '{tidy_fit_stand[ind[8], 15]}']
")

#  nodesep = 1.0 // Increase horizontal spacing between nodes
# Create the full graph string

#ranksep = 0.05
graph_string <- glue("
digraph flowchart {{
  rankdir = LR
  node [fontname = Arial, shape = square, fontsize=11, width=1.15, height=0.75]

  tab1 [label = 'Well-being']
  tab2 [label = 'Green space\\nquality']
  tab3 [label = 'Grassland']
  tab4 [label = 'Arable']
  tab5 [label = 'Woodland']
  tab6 [label = 'Built-up']
  tab7 [label = 'Improved\ngrassland']
  tab8 [label = 'Visit\\nfrequency']
  
  {edges}
  
  {{ rank = same; tab1; tab8 }}
  
  {{ rank = same; tab3; tab4; tab5; tab6;  tab7}}
}}
")

# Render the graph
plot_paths <- grViz(graph_string, width = 800, height = 800)

plot_paths
setwd(Figures_wd)

grViz(graph_string) %>%
    export_svg %>% charToRaw %>% rsvg_png("SEM_paths_stand.png",  width = 1000, height = 800)


## https://cran.r-project.org/web/packages/lavaanPlot/vignettes/Intro_to_lavaanPlot.html
```


## SEM - Number of land covers

```{r sem_num_habs, echo = FALSE}
## Specify model
model_spec <- ' 
# direct effect
             Wellbeing_sat_num ~1+ b2*M1_Q5_comp + b1*visit_freq_bin_num + c*num_habs_wtd + Home_IMD_quint_num + income_num + East + East_Midlands + London + North_East + North_West + South_West + West_Midlands + Yorkshire_and_the_Humber + Gender_2levs + a16_24+ a25_39 + a55_64 + a65 + Ethnicity_cats + Marital_cats + car_cats + Dog + Gen_health_3cats_num + Illnesses + Y2021 + Y2022 + Y2023 + Minimal_restrictions + Outdoor_recreation_limited + First_full_lockdown + Spring + Summer + Autumn
             
           # mediators
  
            M1_Q5_comp ~1+ hq*num_habs_wtd + Home_IMD_quint_num + income_num + East + East_Midlands + London + North_East + North_West + South_West + West_Midlands + Yorkshire_and_the_Humber + Gender_2levs+ a16_24+ a25_39 + a55_64 + a65 + Ethnicity_cats + Marital_cats + car_cats + Dog + Gen_health_3cats_num + Illnesses + Y2021 + Y2022 + Y2023  + Minimal_restrictions + Outdoor_recreation_limited + First_full_lockdown + Spring + Summer + Autumn
            
             visit_freq_bin_num ~ 1+ d*M1_Q5_comp + hv*num_habs_wtd + Home_IMD_quint_num + income_num + East + East_Midlands + London + North_East + North_West + South_West + West_Midlands + Yorkshire_and_the_Humber + Gender_2levs  + a16_24+ a25_39 + a55_64 + a65 + Ethnicity_cats + Marital_cats + car_cats + Dog + Gen_health_3cats_num + Illnesses + Y2021 + Y2022 + Y2023 + Minimal_restrictions + Outdoor_recreation_limited + First_full_lockdown + Spring + Summer + Autumn

            
           # indirect effects (a*b)
           
             hvb1 := hv*b1
             
             hqb2 := hq*b2
             
             hqdb1 := hq*d*b1
             
             ## All indirect
             ttl_indirect_hv := (hv*b1) + (hq*b2) + (hq*d*b1)
             
           # total effects
             totalh1 := (hv*b1) + (hq*b2) + (hq*d*b1) + c
         '

## Fit model
fit <- sem(model_spec, data = mod_data,sampling.weights  = "rescaled_weights")
setwd(Results_wd)
## Create standardised coefficients table
## Presented in supp mats
tidy_fit_stand<-standardizedSolution(fit)


ind<-which(tidy_fit_stand$op== ":=")
pathways<-tidy_fit_stand[ind,] 

col_ind<-grep("pvalue", names(pathways))
pathways$est_stars<-round(pathways$est.std, digits =3)
## Add stars to indicate significance
stars_ind<-grep("stars", names(pathways))
stars_names<-names(pathways)[stars_ind]
for (i in 1:length(col_ind)){
  ind<-which(pathways[col_ind[i]]<0.001)
  pathways[[stars_names[i]]][ind]<-paste0( pathways[[stars_names[i]]][ind], "***")
  ind<-which(pathways[col_ind[i]]<0.01 & pathways[col_ind[i]]>=0.001)
  pathways[[stars_names[i]]][ind]<-paste0( pathways[[stars_names[i]]][ind],"**")
  ind<-which(pathways[col_ind[i]]<0.05 & pathways[col_ind[i]]>=0.01)
  pathways[[stars_names[i]]][ind]<-paste0( pathways[[stars_names[i]]][ind], "*")
}

rm(ind, i, stars_names, stars_ind)

pathways<- pathways %>%
  mutate(conf_int=paste0(round(ci.lower, digits = 3), ",",round(ci.upper, digits = 3))) %>%
  select(rhs,est_stars, conf_int)


write.csv(pathways, "tidy_sem_pathways__num_landcovers_standardised.csv")
print("Standardised pathways - number of land covers")
pathways_flex<-flextable(pathways)
pathways_flex
rm(pathways, pathways_flex)

## There are hundreds of rows, so only included key rows
ind<-grep("M1_Q5_comp|visit_freq_bin_num|Wellbeing_sat_num", tidy_fit_stand$lhs)
tidy_fit_stand<-tidy_fit_stand[ind,]
rm(ind)
tidy_fit_stand<-pivot_wider(tidy_fit_stand,id_cols = rhs, names_from = lhs, values_from = c( est.std,se, pvalue, ci.lower, ci.upper))

cols_green<-grep("M1_Q5_comp", names(tidy_fit_stand))
cols_sat<-grep("Wellbeing", names(tidy_fit_stand))
cols_visit<-grep("visit", names(tidy_fit_stand))
tidy_fit_stand<-tidy_fit_stand[, c(1, cols_green, cols_visit, cols_sat)]
rm(cols_green, cols_visit, cols_sat)

tidy_fit_stand[,2:NCOL(tidy_fit_stand)]<-round(tidy_fit_stand[,2:NCOL(tidy_fit_stand)], digits =3)
## Add stars to indicate significance
col_ind<-grep("pvalue", names(tidy_fit_stand))
tidy_fit_stand$est.stars_Green_space_quality<-round(tidy_fit_stand$est.std_M1_Q5_comp, digits =2)
tidy_fit_stand$est.stars_visit_freq_bin_num<-round(tidy_fit_stand$est.std_visit_freq_bin_num, digits =2)
tidy_fit_stand$est.stars_Wellbeing_sat_num<-round(tidy_fit_stand$est.std_Wellbeing_sat_num, digits =2)

stars_ind<-grep("stars", names(tidy_fit_stand))
stars_names<-names(tidy_fit_stand)[stars_ind]
for (i in 1:length(col_ind)){
  ind<-which(tidy_fit_stand[col_ind[i]]<0.001)
  tidy_fit_stand[[stars_names[i]]][ind]<-paste0( tidy_fit_stand[[stars_names[i]]][ind], "***")
  ind<-which(tidy_fit_stand[col_ind[i]]<0.01 & tidy_fit_stand[col_ind[i]]>=0.001)
   tidy_fit_stand[[stars_names[i]]][ind]<-paste0( tidy_fit_stand[[stars_names[i]]][ind],"**")
  ind<-which(tidy_fit_stand[col_ind[i]]<0.05 & tidy_fit_stand[col_ind[i]]>=0.01)
   tidy_fit_stand[[stars_names[i]]][ind]<-paste0( tidy_fit_stand[[stars_names[i]]][ind], "*")
}

rm(i, col_ind, stars_ind, stars_names)
tidy_fit_stand<-tidy_fit_stand[,c(1:2, 17, 3:7, 18, 8:12, 19, 13:16)]

write.csv(tidy_fit_stand, "tidy_sem_results_standardised.csv")

tidy_fit_stand_flex<-flextable(tidy_fit_stand)
print("Standardised SEM results predicting life satisfaction by number of land covers")
tidy_fit_stand_flex

rm(tidy_fit_stand_flex)

### Prepare unstandardised results table, presented in main manuscript
sum_sem<-summary(fit)
ind<-which(sum_sem$pe$lhs=="hvb1")
unstandard_indirect<-sum_sem$pe[ind:NROW(sum_sem$pe),] 
unstandard_indirect[,6:9]<-round(unstandard_indirect[,6:9], digits = 3)
write.csv(unstandard_indirect, "unstandardised_indirect_totals_num_habs.csv")
rm(sum_sem, ind, unstandard_indirect)

tidy_fit<-tidySEM::table_results(fit , digits = 3)
ind<-grep("M1_Q5_comp|visit_freq_bin_num|Wellbeing_sat_num", tidy_fit$label)
tidy_fit<-tidy_fit[ind,]
rm(ind)
ind<-grep("Variances|Means", tidy_fit$label)
tidy_fit<-tidy_fit[-ind,]
rm(ind)

tidy_fit$Predictor<-NA
tidy_fit$Outcome<-NA
for (i in 1:NROW(tidy_fit)){
  end_char<-unlist(gregexpr(pattern ='\\.',tidy_fit$label[i]))[[1]]
  tidy_fit$Outcome[i]<-substr(tidy_fit$label[i], 1, end_char-1)
  rm(end_char)
  start_char<-unlist(gregexpr(pattern ='\\.',tidy_fit$label[i]))[[2]]
  tidy_fit$Predictor[i]<-substr(tidy_fit$label[i], start_char+1, nchar(tidy_fit$label[i]))
  rm(start_char)
}
tidy_fit$label<-NULL
tidy_fit$Outcome<-gsub("M1_Q5_comp", "Green_qual_comp", tidy_fit$Outcome)

tidy_fit<-pivot_wider(tidy_fit,id_cols = Predictor, names_from = Outcome, values_from = c( est_sig,se, pval,confint))

cols_green<-grep("Green_", names(tidy_fit))
cols_sat<-grep("Wellbeing", names(tidy_fit))
cols_visit<-grep("visit", names(tidy_fit))
tidy_fit<-tidy_fit[, c(1, cols_green, cols_visit, cols_sat)]
rm(cols_green, cols_visit, cols_sat)

tidy_fit_flex<-flextable(tidy_fit) %>%
  colformat_num(j = c(  "pval_Green_qual_comp", "pval_visit_freq_bin_num",   "pval_Wellbeing_sat_num"  ), digits = 3)
print("Untandardised SEM results predicting life satisfaction by number of land covers")
tidy_fit_flex

## save table
setwd(Results_wd)
write.csv(tidy_fit, "tidy_sem_results_unstandardised.csv")
rm(tidy_fit, tidy_fit_flex)

#summary(fit, standardized=TRUE, fit.measures=TRUE)
#fitMeasures(fit, standardized=TRUE)
#modindices(fit,sort=TRUE)

## plot standardised results
## This plot is too complicated though as it includes all variables
## I did it manually in the paper
#p<-lavaanPlot(fit, coefs = TRUE, sig = 0.05, stand = TRUE, stars = "regress", graph_options = list(rankdir = "LR"))

#p<-lavaanPlot2(fit, graph_options 
#p
#rm(p)


#key_vars <- c("Wellbeing_sat_num", "M1_Q5_comp","ACNG_cats_num", "AH_cats_num",
 #             "BMYW_cats_num", "BUAG_cats_num", "IG_cats_num",
  #            "visit_freq_bin_num")

#ind <- match(key_vars, tidy_fit_stand$rhs)

```
<!---BLOCK_LANDSCAPE_STOP--->